### 2024-03-19 Paper/main.tex
first commit

% used template from Overleaf: https://www.overleaf.com/latex/templates/academic-paper/rjttmshldvgg

% weird fix for biblatex from: https://tex.stackexchange.com/questions/568021/package-biblatex-error-patching-addtocontents-failed
\let\latexaddtocontents\addtocontents
\documentclass[10pt]{paper}
\let\addtocontents\latexaddtocontents

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{hyperref}

\usepackage{biblatex} % https://www.overleaf.com/learn/latex/Bibliography_management_in_LaTeX
\addbibresource{main.bib}

\begin{document}

\title{MATH181 Project: Automatic Identification of Nonlinear Systems}
\author{Theo Rode}

% \affiliation{Somewhere}

% \begin{abstract}
% Your abstract.
% \end{abstract}

\maketitle

\section{Introduction}
\label{sec:introduction}
This project discusses the procedure of recovering the underlying equations for the dynamics given noisy data collected by the system. So called ``physics-inspired'' or ``physics-informed'' AI.
The goal of this field is to gain a physical understanding of systems where we can measure various trajectories, but the dynamics are unknown. Though this is additionally useful in situations where complex systems have dynamical properties that can be modeled on a smaller scale. 
In particular, the focus of this project is on discussing the results demonstrated in a paper published in 2016 by Steven Brunton, Joshua Proctor, and Nathan Kutz who propose an algorithm for reconstructing dynamics dubbed SINDy (Sparse Identification of Nonlinear Dynamics) \cite{sindy}.
This first section aims to discuss the field more broadly and relevant papers to the results proposed in the aforementioned paper as well as more generally in the field.

The authors of \cite{sindy} give two foundational papers for recovering the dynamics of nonlinear systems: a paper by Josh Bongard and Hod Lipson \cite{bongard} and one by Michael Schmidt and Hod Lipson \cite{schmidt}, in 2007 and 2009 respectively.
Bongard and Lipson \cite{bongard} outline a method for ``reverse engineering'' the dynamics of nonlinear systems utilizing an active learning system. 
The main process of the algorithm is a technique labeled \textbf{symbolic regression}.
In \cite{bongard}, symbolic regression is made usable for complicated (nonlinear) systems by introducing three concepts: partitioning, automated probing, and snipping. Partitioning is a process by which the algorithm is able to model each of the variables in the system separately using Stochastic optimization. 
Each of the variables are integrated by substituting in representations of the other variables rather than integrating the variables together. This method significantly reduces the overhead when working with high dimensional systems. Automated probing allows the algorithm to explore the system through active learning. After candidate models are created, the algorithm attempts to create many ``tests'' which are judged against their ability to disprove as many of the candidate models as possible. Then, the test which rejects as many of the candidate models as possible is used to judge the performance of all candidate models in order to pick the most capable ones. From this, the next generation of candidate models can be generated. 
Finally, snipping is a process to reduce the complexity of the generated models and prevent over-fitting. In particular, when creating another generation of models, occasionally certain subexpressions will be replaced with a value of the subexpression picked uniformly from its range. This acts to reduce situations where the models will create complex subexpressions which take on narrow ranges of values, demonstrating over-fitting to the data. 
Together, these innovations on the process of symbolic regression allowed Bongard and Lipson to create a framework that was applicable to an array of real-world systems. The framework demonstrated the ability to find nonlinearities and interdependencies as well as an ability to scale successfully. However, the authors note that current limitations include not yet demonstrating scalability to much larger biological models and an inability to work on data where certain variables are unobservable, as a key component of the framework was the active learning \cite{bongard}.

Schmidt and Lipson present a different algorithm for reconstructing dynamics that is still based on \textbf{symbolic regression} \cite{schmidt}. This paper focuses on presenting a new metric for comparing the accuracy of various candidate equations in order to better search for invariants within the system. In particular, once candidate equations are generated (initially randomly from a set of ``building blocks''), the partial derivative pairings of every pair of variables are compared to the numerically calculated partial derivative pairings in order to select the equations which model these pairs the closest. The next generation of equations is then generated from these best equations probabilistically. The algorithm will return a set of equations when they reach a certain accuracy to the observed data, calculated from a subset of the data randomly selected to be withheld from training. 
Furthermore, these equations are prioritized according to a measured parsimony, effectively complexity which is calculated by the number of terms in the expression. The authors were able to demonstrate that this algorithm could reconstruct invariants from numerous physical systems effectively. Additionally, they noticed that with a limited set of building blocks, the algorithm found approximations to functions like sines and cosines, utilizing the available building blocks, when such functions were part of the physical invariant \cite{schmidt}.

% TALK ABOUT MORE RECENT PAPER?

% mention LASSO: https://watermark.silverchair.com/jrsssb_58_1_267.pdf?token=AQECAHi208BE49Ooan9kkhW_Ercy7Dm3ZL_9Cf3qfKAc485ysgAAA3swggN3BgkqhkiG9w0BBwagggNoMIIDZAIBADCCA10GCSqGSIb3DQEHATAeBglghkgBZQMEAS4wEQQMUUUguuXeXSXLKrHyAgEQgIIDLjjGy45TLem5-SWBsiKqth_ATlBiN1U8oB2jwRawwKAQLhSBq9mr6Xxoy5NWpIW4ICk-qvgW4vlMPUFgp3aXI1CPO7BCP5VER8ruRsVHe-xFxsJrz1Idh0wPazgvEt6cHJfNxeEWOxiBPBYyPMSESASwKHfX4EQxoq_Au2Bzkg6gFRWiGBSestTCekla3yBbmJ9FMWqtL0hVt0LtXXwf81ICM7qX_y4YW0ZKOUS2M9z2EEIMgWCkfeivpJT0CJi8CWfL7oorAsCpsu_wxGucDzNm_Ki_SqlaNZAU-mI3iVIxr4FUCWJxgh8mfeHxCJttaC1p97U5TX3OTzL_S71k4-4DNrWUaGhKgRe2QEXZg8SLWnsRolTN6MBmtlfstqIoMP4PPsaIJ_93YWxRALnL_pdknBTh2edgos_NVDt6nMC41LoCepoI8cSD0BgcJo3L_v3Fa4KOnVHpfLED7PCgj_mT7UY2d4dJlO_3ryWWXa_NhgGbXUywx8KOJzC0M1O0ZAEo0pmz50mMzp0XyVQX6sl3uCHzDB8zHWfI8-BHBzC5dYDHKeGx7xS8H4wws5EriZX_jeHIG4NYUTbCLV0IaVCx4nxTrc6gglm8D2aqlBjI52KHj7iIi78EKZ7pcrgfJ6-RA2rb2435a--KHrXE1S5E4feJA2KWhx7VBEn-t53uszHD7bE3sOrHU7qHDzYKWeuk3T_ewVJuyE8_-P7tLVtWoSKxvsqT1mR4inR6UKmJbHjyTH0HV2QQ6ybtztDj7hrgVPQROkmBMhURkCaGMJHTFeYtdF9W4ZGb7O432f22h7ousNc5dDIAAyGtxGI6doK4bS35eWPzqVMZ5Q4D9WIncF_ehYujzLdosbyNyZLt9SPwaPCBfHwwXCxyDkArH_MWjjOyz-h6D0JxXRyTOyZhw9vbNp8vkpccU0W1zNfmyYn8SkDQJwpN5L1mUpPXeASQb4eH8rE6VttkD09Lmqv4hy502xE-88dYoKVoOToavtAVT9nc-ARwnQ4eyS1dkmPBfy9KOlIz7WHvIg0XFbNoG5AoMjCya6vdfYmDLgNJuhvRVilIhFkuuxMw2cc
% supposedly helpful for sparse regression?

% talk about advances in compressed sensing seen here: https://journals.aps.org/prl/pdf/10.1103/PhysRevLett.106.154101

\section{Mathematical Background}
For the SINDy algorithm, the authors aimed to reframe the problem of recovering nonlinear dynamics using \textbf{sparse regression} and \textbf{compressed sensing} \cite{sindy}. Both sparse regression and compressed sensing broadly refer to the process of finding a regression solution to a problem such that the solution is sparse in some space \cite{sindy}. 
Brunton et al. relate that utilizing sparse regression is a strategy to reduce the noise present in the fitting of systems \cite{sindy}. The particular assumptions for sparse regression come from the idea that in most cases, the dynamics for a particular system will be governed by a small set of given basis functions. Therefore, the sparsity also gives advantages for computation as we can increase the size of the function space dramatically without needing significantly more computation \cite{sindy}.

% mention LASSO here as alternative method for sparse regression
The authors of \cite{sindy} propose an iterative algorithm for sparse regression. In particular, they start with a least-squares fit to the data, and then iteratively remove coefficients below a given threshold. By refitting with the remaining, nonzero terms iteratively, the algorithm can arrive at a sparse solution \cite{sindy}.

The SINDy algorithm relies on the availability of both sampled data, $\boldsymbol X$, and the sampled derivative, $\boldsymbol{\dot X}$. However, the authors note that the availability of derivative measurements are not guaranteed and therefore propose using the \textbf{total variation regularized derivative} to mitigate the noise created from numerically calculating $\boldsymbol {\dot X}$ from $\boldsymbol X$ \cite{sindy}. In particular, they cite the algorithm used by Rudin et al. \cite{rudin}. 
Here, Rudin et al. use a framework for computing a desired, denoised output, $u$, from a noisy input, $u_0$, by assuming that $u = u_0 + n$ for some white noise function $n$. It is assumed that $n$ has a mean of $0$ with some given standard deviation. 
The minmization problem corresponds to minimizing $\int_\Omega \sqrt{u_x^2 + u_y^2} \, \mathrm d A$, which is contrained by $\int_\Omega u \, \mathrm dA = \int_\Omega u_0 \, \mathrm dA$ under the assumption of the additive white noise. It is then proposed to solve for $u$ through either an iterative algorithm (i.e. simulated annealing) or, preferably, a PDE solver to find local minimum \cite{rudin}.

In order to address the computational difficulties present in higher-dimensional problems, Brunton et al. suggest using \textbf{proper orthogonal decomposition (POD)} in order to perform dimension reduction \cite{sindy}. 
Berkooz at el. outline the process of POD on a space of functions \cite{berkooz}. In particular, POD aims to produce a set of vectors (eigenfunctions) and corresponding eigenvalues which best represent a given vector field with coefficients that are uncorrelated (part of a random process) \cite{berkooz}. 
% https://arc.aiaa.org/doi/epdf/10.2514/1.J058809 (POD)

\subsection{SINDy}
The most basic systems considered for the algorithm SINDy are those of the form 
\[ \frac{\mathrm d}{\mathrm dt} \boldsymbol x(t) = \boldsymbol f (\boldsymbol x(t)). \]
In order to use the concepts of sparse regression and compressed sensing, discussed above, the authors assume that $\boldsymbol f$ is sparse in some function space \cite{sindy}.
The state vector, $\boldsymbol x(t)$, is collected over some time period and $\boldsymbol {\dot x}$ is either sampled alongside $\boldsymbol x(t)$ or numerically calculated from it. 
These samplings create the following matrices: 
\[ \boldsymbol X = \begin{bmatrix}
	\boldsymbol x^T(t_1) \\ \boldsymbol x^T(t_2) \\ \vdots \\ \boldsymbol x^T(t_m)
\end{bmatrix}, \]  
and the immediately following $\boldsymbol {\dot X}$. We can then construct a library of candidate functions: 
\[  \Theta(\boldsymbol X) = \begin{bmatrix} \mid & \mid & \mid & \mid &  & \mid & \mid & \\ 1 & \boldsymbol X & {\boldsymbol X}^{P_2} & {\boldsymbol X}^{P_3} & \cdots & \sin{(\boldsymbol X)} & \cos{(\boldsymbol X)} & \cdots \\ \mid & \mid & \mid & \mid & & \mid & \mid & \end{bmatrix}.  \]
Each column of $\Theta(\boldsymbol X)$, therefore, represents a candidate function for $\boldsymbol f$. This therefore sets up the sparse regression problem 
\[ \boldsymbol {\dot X} = \Theta(\boldsymbol X)\Xi. \]

% \section{}
% \label{sec:examples}

% \subsection{Sections}

% \begin{acknowledgments}

% We thank\dots

% \end{acknowledgments}

\newpage
\printbibliography

\end{document}

### 2024-04-10 Paper/main.tex
edits
code and paper section 3 draft

@@
 \usepackage{hyperref}
+\usepackage{float}
+
+\graphicspath{ {./images/} }
 
@@
 \addbibresource{main.bib}
+
+% Code blocks
+\usepackage[theme=default]{jlcode}
+% \usepackage{listings, xcolor}
+
+% \definecolor{codegreen}{rgb}{0,0.6,0}
+% \definecolor{codegray}{rgb}{0.5,0.5,0.5}
+% \definecolor{codepurple}{rgb}{0.58,0,0.82}
+% \definecolor{backcolour}{rgb}{0.95,0.95,1}
+
+% \lstdefinestyle{mystyle}{
+%     backgroundcolor=\color{backcolour},   
+%     commentstyle=\color{codegreen},
+%     keywordstyle=\color{magenta},
+%     numberstyle=\tiny\color{codegray},
+%     stringstyle=\color{codepurple},
+%     basicstyle=\ttfamily\footnotesize,
+%     breakatwhitespace=false,         
+%     breaklines=true,                 
+%     captionpos=b,                    
+%     keepspaces=true,                 
+%     numbers=left,                    
+%     numbersep=5pt,                  
+%     showspaces=false,                
+%     showstringspaces=false,
+%     showtabs=false,                  
+%     tabsize=4
+% }
+
+% \lstset{style=mystyle}
 
@@
 
-The SINDy algorithm relies on the availability of both sampled data, $\boldsymbol X$, and the sampled derivative, $\boldsymbol{\dot X}$.
-However, the authors note that the availability of derivative measurements are not guaranteed and therefore propose using the \textbf{total variation regularized derivative} to mitigate the noise created from numerically calculating $\boldsymbol {\dot X}$ from $\boldsymbol X$ \cite{sindy}.
+The SINDy algorithm relies on the availability of both sampled data, $\mathbf X$, and the sampled derivative, $\mathbf{\dot X}$.
+However, the authors note that the availability of derivative measurements are not guaranteed and therefore propose using the \textbf{total variation regularized derivative} to mitigate the noise created from numerically calculating $\mathbf {\dot X}$ from $\mathbf X$ \cite{sindy}.
 In particular, they cite the algorithm used by Rudin et al.
@@
 
-In order to address the computational difficulties present in higher-dimensional problems, Brunton et al.
+% In order to address the computational difficulties present in higher-dimensional problems, Brunton et al.
 suggest using \textbf{proper orthogonal decomposition (POD)} in order to perform dimension reduction \cite{sindy}.
-Berkooz at el.
+% Berkooz at el.
 outline the process of POD on a space of functions \cite{berkooz}.
 In particular, POD aims to produce a set of vectors (eigenfunctions) and corresponding eigenvalues which best represent a given vector field with coefficients that are uncorrelated (part of a random process) \cite{berkooz}.
-% https://arc.aiaa.org/doi/epdf/10.2514/1.J058809 (POD)
+% % https://arc.aiaa.org/doi/epdf/10.2514/1.J058809 (POD)
 
-\subsection{SINDy}
+\subsection{SINDy} \label{sec:SINDy}
 The most basic systems considered for the algorithm SINDy are those of the form 
-\[ \frac{\mathrm d}{\mathrm dt} \boldsymbol x(t) = \boldsymbol f (\boldsymbol x(t)). \]
-In order to use the concepts of sparse regression and compressed sensing, discussed above, the authors assume that $\boldsymbol f$ is sparse in some function space \cite{sindy}.
-The state vector, $\boldsymbol x(t)$, is collected over some time period and $\boldsymbol {\dot x}$ is either sampled alongside $\boldsymbol x(t)$ or numerically calculated from it. 
+\[ \frac{\mathrm d}{\mathrm dt} \mathbf x(t) = \mathbf f (\mathbf x(t)). \]
+In order to use the concepts of sparse regression and compressed sensing, discussed above, the authors assume that $\mathbf f$ is sparse in some function space \cite{sindy}.
+The state vector, $\mathbf x(t)$, is collected over some time period and $\mathbf {\dot x}$ is either sampled alongside $\mathbf x(t)$ or numerically calculated from it. 
 These samplings create the following matrices: 
-\[ \boldsymbol X = \begin{bmatrix}
-	\boldsymbol x^T(t_1) \\ \boldsymbol x^T(t_2) \\ \vdots \\ \boldsymbol x^T(t_m)
+\[ \mathbf X = \begin{bmatrix}
+	\mathbf x^T(t_1) \\ \mathbf x^T(t_2) \\ \vdots \\ \mathbf x^T(t_m)
+\end{bmatrix} = \begin{bmatrix}
+	x_1(t_1) & x_2(t_1) & \cdots & x_n(t_1) \\
+	x_1(t_2) & x_2(t_2) & \cdots & x_n(t_2) \\
+	\vdots & \vdots & \ddots & \vdots \\ 
+	x_1(t_m) & x_2(t_m) & \cdots & x_n(t_m)
 \end{bmatrix}, \]  
-and the immediately following $\boldsymbol {\dot X}$. We can then construct a library of candidate functions: 
-\[  \Theta(\boldsymbol X) = \begin{bmatrix} \mid & \mid & \mid & \mid &  & \mid & \mid & \\ 1 & \boldsymbol X & {\boldsymbol X}^{P_2} & {\boldsymbol X}^{P_3} & \cdots & \sin{(\boldsymbol X)} & \cos{(\boldsymbol X)} & \cdots \\ \mid & \mid & \mid & \mid & & \mid & \mid & \end{bmatrix}.
+and the immediately following $\mathbf {\dot X}$. We can then construct a library of candidate functions: 
+\[  \Theta(\mathbf X) = \begin{bmatrix} \mid & \mid & \mid & \mid &  & \mid & \mid & \\ 1 & \mathbf X & {\mathbf X}^{P_2} & {\mathbf X}^{P_3} & \cdots & \sin{(\mathbf X)} & \cos{(\mathbf X)} & \cdots \\ \mid & \mid & \mid & \mid & & \mid & \mid & \end{bmatrix}.
 \]
-Each column of $\Theta(\boldsymbol X)$, therefore, represents a candidate function for $\boldsymbol f$. This therefore sets up the sparse regression problem 
-\[ \boldsymbol {\dot X} = \Theta(\boldsymbol X)\Xi. \]
+Here, $\mathbf X^{P_2}$ represents the quadratic nonlinearities in $\mathbf f$, in particular: 
+\[ \mathbf X^{P_2} = \begin{bmatrix}
+	x_1^2(t_1) & x_1(t_1)x_2(t_1) & \cdots & x_1(t_1)x_n(t_1) & x_2^2(t_1) & \cdots & x_n^2(t_1) \\
+	x_1^2(t_2) & x_1(t_2)x_2(t_2) & \cdots & x_1(t_2)x_n(t_2) & x_2^2(t_2) & \cdots & x_n^2(t_2) \\
+	\vdots & \vdots & \ddots & \vdots & \vdots & \ddots & \vdots \\
+	x_1^2(t_m) & x_1(t_m)x_2(t_m) & \cdots & x_1(t_m)x_n(t_m) & x_2^2(t_m) & \cdots & x_n^2(t_m) \\
+\end{bmatrix}. \]
+Similarly, $\sin{(\mathbf X)}$ would be 
+\[ \sin{(\mathbf X)} = \begin{bmatrix}
+	\sin(x_1(t_1)) & \sin(x_2(t_1)) & \cdots & \sin(x_n(t_1)) \\ 
+	\sin(x_1(t_2)) & \sin(x_2(t_2)) & \cdots & \sin(x_n(t_2)) \\
+	\vdots & \vdots & \ddots & \vdots \\ 
+	\sin(x_1(t_m)) & \sin(x_2(t_m)) & \cdots & \sin(x_n(t_m))
+\end{bmatrix}. \]
+Therefore, each column of $\Theta(\mathbf X)$ represents a candidate function for $\mathbf f$. From this, we set up the sparse regression problem
+\[ \mathbf {\dot X} = \Theta(\mathbf X)\mathbf \Xi. \]
+In particular, $\mathbf \Xi = \begin{bmatrix}
+	\boldsymbol \xi_1 & \boldsymbol \xi_2 & \cdots & \boldsymbol \xi_n
+\end{bmatrix}$ where each $\boldsymbol \xi_i$ is a sparse vector dictating which functions in the function library are active for each of the row equations in $\mathbf f$.
+The sparse regression problem is an iterative algorithm that iteratively thresholds out coefficients in $\mathbf \Xi$ under some sparsity parameter, $\lambda$, and then refits the problem on the remaining functions.
+
+The authors additionally suggest a slight modification to the algorithm in order to detect bifurcations present in a system.
+In particular, the authors appended the bifurcation parameter to the dynamics:
+\begin{equation} \label{eq:sindy_with_bifurcation}
+	\begin{split}
+		\mathbf {\dot x} &=  \mathbf{f}(\mathbf x; \mu), \\
+		\dot \mu &= 0.
+	\end{split}
+\end{equation}
+Then, by sampling data from different values of $\mu$, it is possible for SINDy to reconstruct the system from combinations of $\mathbf x$ as well as $\mu$.
+In turn, the system can then find the dynamics present with changes in $\mu$, and hence bifurcations.
+
+\section{Results}
+\subsection{Code}
+The main object in recreating the results presenting in the paper was writing a codebase that is able to recreate the SINDy algorithm. 
+I wrote the code in the Julia Programming Language \cite{julia} and with all plotting done in PlotlyBase.jl \cite{PlotlyBase.jl}.
+
+All data used to train the SINDy model was collected by integrating using ordinary differential equation (ODE) solvers provided by the DifferentialEquations.jl \cite{rackauckas2017differentialequations} package.
+For the numerical stability of the model, data was collected at fixed timesteps, as shown in Listing \ref{lorenz_data} for the Lorenz system.
+
+\jlinputlisting[language = Julia, caption = {Lorenz system data simulation}, label = {lorenz_data}, firstline = 9, lastline = 14]{../Code/DynamicsRecovery/src/Systems/lorenz.jl}
+
+Additionally, noise sampled from a standard normal distribution was scaled by a noise parameter and added to the collected data before SINDy was trained on it.
+This code utilized the Distributions.jl \cite{JSSv098i16}\cite{Distributions.jl-2019} package to provide the normal distribution.
+Once the data was collected and noise applied, the program constructed the data matrix, $\mathbf X$, and the corresponding derivative matrix, $\mathbf {\dot X}$.
+Differentiation is done in one of two ways, either through direct numerical differentiation, using Interpolations.jl \cite{Interpolations.jl}, or using the total-variation regularization derivative, provided by NoiseRobustDifferentiation.jl \cite{chartrand2011numerical}\cite{NoiseRobustDifferentiation.jl}.
+Using a linear interpolation to compute the derivatives had the additional benefit of being more stable when samples were not taken with constant timestamps, and deviates in approach from the code written by Brunton et al.
+\cite{sindy}.
+The code for constructing the data and derivative libraries is shown in Listing \ref{X_Xdot_construction}.
+
+% https://tex.stackexchange.com/questions/73231/avoid-page-breaks-in-lstlistings
+% https://tex.stackexchange.com/questions/39017/how-to-influence-the-position-of-float-environments-like-figure-and-table-in-lat
+\jlinputlisting[language = Julia, caption = {Data and derivative library construction}, label = {X_Xdot_construction}, firstline = 68, lastline = 95, float, floatplacement = tb]{../Code/DynamicsRecovery/src/SINDy/data_ingestion.jl}
+
+Utilizing the data matrix, $\mathbf X$, it is then simple to construct the function library, $\mathbf \Theta(\mathbf X)$.
+Unlike the original paper \cite{sindy}, this implementation allows for arbitrary functions to be used and provides a framework for easily expanding the type and quantity of functions used. 
+In particular, along with the potential to fit arbitrary functions, the generation of polynomial terms was done generally to support arbitrary degree polynomials utilizing functions Combinatorics.jl \cite{Combinatorics.jl}.
+
+Finally, the sparse regression algorithm to compute $\mathbf \Xi$ is the same process as outlined by Brunton et al.
+\cite{sindy}.
+In particular, the starting point for the iterative algorithm is a least-squares solution to the problem using a standard regression.
+Then, over $k$ iterations, coefficients in $\mathbf \Xi$ which are less than the sparsity parameter, $\lambda$, are dropped and replaced with zero.
+In each of these iterations, the regression is then recomputed with only the nonzero entries.
+This code is presented in Listing \ref{sparse_regression}.
+
+\jlinputlisting[language = Julia, caption = {Sparse regression}, label = {sparse_regression}, firstline = 3, lastline = 23, float, floatplacement = ptb]{../Code/DynamicsRecovery/src/SINDy/sparse_regression.jl}
+
+The resulting system defined by $\mathbf \Xi$ can then be solved using the same methods as when collecting data for the original system.
+The governing equations are constructed using the same function generation from the library construction in order to ensure complete generality.
+
+\subsection{The Lorenz Attractor} \label{sec:lorenz_results}
+In replicating the results of Brunton et al., I first pursued replicating the success they found in recoverying the dynamics present in the chaotic Lorenz System \cite{sindy}\cite{lorenz1963deterministic}.
+The dynamics for this system are governed by the following equations, 
+\begin{equation}\label{eq:lorenz}
+\begin{split}
+	\dot x &= \sigma(y - x), \\
+	\dot y &= x(\rho - z) - y, \\
+	\dot z &= xy - \beta z.
+\end{split}
+\end{equation}
+I used the same initial conditions and parameters that Brunton et al.
+\cite{sindy} used for their demonstrations.
+In particular, $u_0 = (-8, 7, 27)$ and parameters $(\sigma, \rho, \beta) = \left( 10, 28, \frac 83 \right)$.
+Figure \ref{fig:lorenz_system_actual} shows the actual system with these parameters and initial condition.
+
+\begin{figure}[h]
+	\caption{Lorenz system}
+	\label{fig:lorenz_system_actual}
+
+	\centering
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{lorenz_actual_graph.png}
+\end{figure}
+
+I ran the SINDy algorithm on both data with noise of magnitude $\eta = 0.01$ and $\eta = 0.1$.
+Of interest is the system with $\eta = 0.1$ was only able to converge on a solution when the derivative was computed using the total-variation regularization derivative.
+For a function basis, I chose a basis comprised of all 7th-degree polynomial terms and all sines and cosines of the form $\sin{(ku_i)}$ and $\cos{(ku_i)}$ for all $\{u_i\} = \{x,y,z\}$ and integer $k$ from $1$ to $10$.
+This created a basis of $180$ possible functions.
+Further, the sparsification parameter was chosen to be $\lambda = 0.25$ with 10 iterations for sparse regression.
+Integration of the input data was done over a timespan from $0$ to $100$ with $dt = 0.001$. 
+The resulting systems from $\eta = 0.01$ are shown in Figure \ref{fig:lorenz_system_found_001} and the system resulting from $\eta = 0.1$ is shown in Figure \ref{fig:lorenz_system_found_01}.
+
+\begin{figure}[h]
+	\caption{Discovered Lorenz system with noise $\eta = 0.01$}
+	\label{fig:lorenz_system_found_001}
+
+	\centering 
+	\begin{minipage}{0.47\textwidth}
+		\begin{center}
+			\includegraphics[width = \textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{lorenz_found_001_normal.png}
+
+			With standard derivative calculation
+		\end{center}
+	\end{minipage}%
+	\begin{minipage}{0.47\textwidth}
+		\begin{center}
+			\includegraphics[width = \textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{lorenz_found_001_tvdiff.png}
+
+			With total-variation regularization derivative
+		\end{center}
+	\end{minipage}
+\end{figure}
+
+\begin{figure}[h]
+	\caption{Discovered Lorenz system with noise $\eta = 0.1$ and total-variation regularization differentiation}
+	\label{fig:lorenz_system_found_01}
+
+	\centering
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{lorenz_found_01_tvdiff.png}
+\end{figure}
+
+We see that the SINDy algorithm was able to effectively capture the attracting dynamics present in the Lorenz system in all cases.
+Furthermore, for the standard derivative and noise $\eta = 0.01$, the discovered system had the form
+\begin{equation} \label{eq:found_lorenz_001}
+	\begin{split}
+		\dot x &= -9.982573809940325x + 9.999536628579511y, \\
+	\dot y &= 27.573169299598813x - 0.8370109395705518y - 0.98935201514641xz, \\
+	\dot z &= -2.660754272317803z + 0.9988807483584906xy.
+	\end{split}
+\end{equation}
+Comparing this result to the actual system (Equation \ref{eq:lorenz}), we see that the discovered system has perfectly identified the polynomial terms in the system with coefficients that are almost identical.
+We see similar strength in identifying the system for $\eta = 0.01$ (Equation \ref{eq:found_lorenz_001_tv}) and $\eta = 0.1$ (Equation \ref{eq:found_lorenz_01_tv}) systems with total-variation regularization derivatives.
+\begin{equation} \label{eq:found_lorenz_001_tv}
+	\begin{split}
+		\dot x &= -9.946417397865872x + 9.97621578174998y, \\
+		\dot y &= 27.0485300793758x - 0.670689440675418y - 0.976667757332429xz, \\
+		\dot z &= -2.6495215942228163z + 0.996381152512881xy.
+	\end{split}
+\end{equation}
+\begin{equation} \label{eq:found_lorenz_01_tv}
+	\begin{split}
+		\dot x &= -9.805048724434341x + 9.835722669096466y, \\
+		\dot y &= 25.92133086771059x - 0.433587521465246y - 0.946115512156319xz, \\
+		\dot z &= -1.930341755171950 - 2.54324607967731z + 0.983562354075398xy.
+	\end{split}
+\end{equation}
+
+We do see a forcing term introduced in the higher noise, $\eta = 0.1$, system for $\dot z$ which represents a term not present in actual system or the other two discovered systems.
+Though decreased performance is expected with higher noise.
+
+\subsection{Bifurcations: The Hopf normal form}
+In addition to SINDy's ability to extract the system dynamics from the chaotic Lorenz attractor (\ref{sec:lorenz_results}), Section \ref{sec:SINDy} discussed how Brunton et al.
+discussed a modification to SINDy which would allow the detection of bifurcations in a system \cite{sindy}.
+Similar to the authors, I will demonstrate this using the Hopf normal form:
+\begin{equation} \label{eq:hopf_normal}
+	\begin{split}
+		\dot x &= \mu x - \omega y - Ax(x^2 + y^2), \\
+		\dot y &= \omega x +\mu y - Ay(x^2 + y^2).
+	\end{split}
+\end{equation} 
+While $\mu$ is the bifurcation parameter and will be varried, I will take $\omega = A = 1$.
+In order for SINDy to discover the bifurcation in its system, we have to collect data over a range of $\mu$ values.
+In particular, I collected data for 16 values of $\mu$ between $-0.2$ and $0.55$, with a Hopf bifurcation occurring when $\mu = 0$.
+For negative values of $\mu$, I collected data with the initial condition $(x_0,y_0) = (2,0)$, while for positive values data was collected both for this initial condition and for $(x_0, y_0) = (0.01, 0)$ in order to capture the limit cycle behavior.
+Further, all collected data was given noise of magnitude $\eta = 0.005$.
+
+In order to account for multiple orbits worth of data, the derivatives for each orbit were calculated separately using the total-variation regularization derivative.
+Then, the $\mathbf X$ and $\mathbf {\dot X}$ matrices for all orbits were combined into a single data and derivative matrix.
+These could then be passed through SINDy as previously.
+For this example, a basis of all polynomials through 5th degree was used, with sparsity parameter $\lambda = 0.25$ and $10$ iterations of the sparse regression.
+Figure \ref{fig:discovered_hopf_0005} shows the discovered system as various values of $\mu$ and its ability to detect the Hopf bifurcation.
+
+\begin{figure}[h]
+	\caption{Discovered Hopf bifurcation. Blue orbits start at $(x_0, y_0) = (2,0)$ and red orbits start at $(x_0, y_0) = (0.01, 0)$.}
+	\label{fig:discovered_hopf_0005}
+
+	\centering
+
+	\includegraphics[width = 0.7\textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{found_hopf_bifurcation_0005.pdf}
+\end{figure}
+
+Furthermore, SINDy found the system to be given by
+
+\begin{equation}\label{eq:discovered_hopf_0005}
+	\begin{split}
+		\dot x &= -0.9916y + 0.9314\mu x - 0.9178x^3 - 0.9178xy^2 - 0.3081x^4y, \\
+		\dot y &= 0.9972x + 0.9926\mu y - 0.9811x^2y - 0.9814y^3.
+	\end{split}
+\end{equation}
+Here we notice that barring the $-0.3081x^4y$ term in the equation for $\dot x$, the algorithm was able to identify the constants remarkably well and the nonlinear terms accurately. 
+Though, its important to note that depending on the noise added to the system, the resulting system can be significantly worse.
+In particular, Equation \ref{eq:bad_discovered_hopf_0005} resulted from the same parameters but with different noise applied.
+\begin{equation}\label{eq:bad_discovered_hopf_0005}
+	\begin{split}
+		\dot x &= -0.9971y + 0.8704\mu x - 0.8617x^3 - 0.9177xy^2 + 0.9186\mu x^2 y  - 0.2853 xy^3 \\
+		&\qquad - 0.9918 \mu x y^2 - 0.8546 x^4y + 1.2614 x^3y^2 - 1.0363 x^2y^3 + 1.0065 xy^4 \\ &\qquad + 0.5446\mu y^3 x, \\
+		\dot y &= 0.9968x + 0.9930\mu y - 0.9807x^2y - 0.9822 y^3.
+	\end{split}
+\end{equation}
+Interestingly, while $\dot y$ remained stable, $\dot x$ tends to me less stable.
+It is important to note, that while there are many additional higher-order polynomial terms, the qualatative behavior of the system is identical, still finding a Hopf bifurcation.
 

### 2024-04-10 Code/DynamicsRecovery/src/DynamicsRecovery.jl

@@ -1,0 +1,21 @@
+module DynamicsRecovery
+
+include("Utils/Utils.jl")
+using .Utils
+export construct_polynomials
+export print_constructed_system
+
+include("SINDy/SINDy.jl")
+using .SINDy
+export constructX, Θ, sparse_regression
+export TvDiffParams
+
+include("Systems/Systems.jl")
+using .Systems
+export hopf_normal!
+export lorenz_data, lorenz!
+export add_noise_to_sample
+export solve_constructed_system
+
+
+end # module DynamicsRecovery

### 2024-04-10 Code/DynamicsRecovery/src/SINDy/SINDy.jl

@@ -1,7 +1,17 @@
 module SINDy 
 
 export constructX
+export TvDiffParams
 
 include("data_ingestion.jl")
 
+export Θ 
+
+include("library_construction.jl")
+
+export sparse_regression
+
+include("sparse_regression.jl")
+
 end # module SINDy
+

### 2024-04-10 Code/DynamicsRecovery/src/SINDy/data_ingestion.jl

@@ -1,10 +1,13 @@
 using NoiseRobustDifferentiation
+using Interpolations
 
 const TVDIFFPARAMS_ITERATIONS::Integer = 100
 const TVDIFFPARAMS_ALPHA::Real = 1e-1
 const TVDIFFPARAMS_SCALE::String = "small"
 const TVDIFFPARAMS_EPSILON::Real = 1e-6
 const TVDIFFPARAMS_PRECOND = "none"
+const TVDIFFPARAMS_PERFORM_TVDIFF = false
+const TVDIFFPARAMS_DIFF_KERNEL = "abs"
 
 """
 Struct holding parameters for total variation regularization
@@ -16,15 +19,9 @@ struct TvDiffParams
     scale::String 
     ε::Real
     precond::String
+    perform_tvdiff::Bool
+    diff_kernel::String
 end # struct TvDiffParams
-
-"""
-    TvDiffParams() -> TvDiffParams
-
-Default initialization for `TvDiffParams`.
-
-"""
-TvDiffParams() = TvDiffParams(TVDIFFPARAMS_ITERATIONS, TVDIFFPARAMS_ALPHA, TVDIFFPARAMS_SCALE, TVDIFFPARAMS_EPSILON, TVDIFFPARAMS_PRECOND)
 
 """
     TvDiffParams(; iterations = 100, α = 1e-1, scale = "small", ε = 1e-6, precond = "none") -> TvDiffParams
@@ -32,7 +29,7 @@ TvDiffParams() = TvDiffParams(TVDIFFPARAMS_ITERATIONS, TVDIFFPARAMS_ALPHA, TVDIF
 Keyword argument initialization for `TvDiffParams`.
 
 """
-TvDiffParams(; iterations::Integer = TVDIFFPARAMS_ITERATIONS, α::Real = TVDIFFPARAMS_ALPHA, scale::String = TVDIFFPARAMS_SCALE, ε::Real = TVDIFFPARAMS_EPSILON, precond::String = TVDIFFPARAMS_PRECOND) = TvDiffParams(iterations, α, scale, ε, precond)
[…]

### 2024-04-10 Code/DynamicsRecovery/src/SINDy/library_construction.jl

@@ -1,4 +1,7 @@
 using LinearAlgebra 
+using Combinatorics 
+
+using DynamicsRecovery.Utils
 
 """
     Θ(X; polynomials, functions) -> Matrix{Float64}
@@ -7,33 +10,32 @@ Constructs library of functions ``\\boldsymbol \\Theta (\\boldsymbol X)`` with d
 
 """
 function Θ(X::Matrix{Float64}; 
-    polynomials::Vector{Integer} = [], 
-    functions::Vector{Function} = [],
-    functions1::Vector{Function} = []
-)
+    polynomials::Vector{T} = [], 
+    functions = [],
+    functions1 = []
+) where T <: Integer
     if length(polynomials) == 0 && length(functions) == 0 && length(functions1) == 0 
         throw(ArgumentError("At least one candidate function needs to be supplied"))
     end # if
 
-    # system dimension is important 
-    dimension = size(X)[2]
-
     # vector to hold all candidate functions 
     function_library::Vector{Matrix{Float64}} = []
 
-    # construct polynomial parts of the library 
-    for n in polynomials 
-        # n = 0 and n = 1 are special cases 
-        if n == 0
-            push!(function_library, ones(size(X))) # constants
-        end # if 
-        if n == 1 
-            push!(function_library, X) # linear occurances 
-        end # if
-        
-        
+    polynomial_functions = construct_polynomials(polynomials, size(X)[2])
 
-    end # for n
-    
+    append!(functions, polynomial_functions)
+
+    for func in functions 
+        push!(function_library,
+            hcat([func(X[i, :]...) for i in 1:size(X)[1]]) # hcat is to convert to matrix 
+        )
+    end # for func
+
+    # for functions1, just apply the function to all items in X 
+    for func1 in functions1
+        push!(function_library, func1.(X))
+    end # for func1
+
+    hcat(function_library...)
 end # function Θ
 

### 2024-04-10 Code/DynamicsRecovery/src/SINDy/sparse_regression.jl

@@ -1,0 +1,23 @@
+using LinearAlgebra
+
+function sparse_regression(Θ::Matrix{Float64}, Xdot::Matrix{Float64}, λ::Float64, kmax::Integer) 
+    # create initial guess for Xi as just regression
+    Ξ = Θ\Xdot
+
+    for _ in 1:kmax 
+        # find coefficients that are less than λ 
+        small_coefficients = abs.(Ξ) .< λ
+
+        # set small coefficients to 0 
+        Ξ[small_coefficients] .= 0
+
+        # now individually run regression on non-zero coefficients
+        for n in 1:(size(Xdot)[2]) # loop through all state dimensions 
+            nonsmall = .!small_coefficients[:, n]
+            
+            Ξ[nonsmall, n] = Θ[:, nonsmall]\Xdot[:, n]
+        end # for n
+    end # for k 
+
+    Ξ
+end # function sparse_regression

### 2024-04-10 Code/DynamicsRecovery/src/Systems/Systems.jl

@@ -1,0 +1,19 @@
+module Systems
+
+export lorenz_data, lorenz!
+
+include("lorenz.jl")
+
+export hopf_normal!
+
+include("hopf.jl")
+
+export add_noise_to_sample
+
+include("utils.jl")
+
+export solve_constructed_system
+
+include("solve_constructed_system.jl")
+
+end # module Systems

### 2024-04-10 Code/DynamicsRecovery/src/Systems/hopf.jl

@@ -1,0 +1,7 @@
+function hopf_normal!(du, u, p, t)
+    # μ: p[1], ω: p[2], A: p[3]
+    
+    du[1] = p[1]*u[1] - p[2]*u[2] - p[3]*u[1]*(u[1]^2 + u[2]^2)
+    du[2] = p[2]*u[1] + p[1]*u[2] - p[3]*u[2]*(u[1]^2 + u[2]^2)
+end # function hopf_normal!
+

### 2024-04-10 Code/DynamicsRecovery/src/Systems/lorenz.jl

@@ -1,0 +1,23 @@
+using DifferentialEquations
+
+function lorenz!(du, u, p, t)
+    du[1] = p[1] * (u[2] - u[1])
+    du[2] = u[1] * (p[2] - u[3]) - u[2]
+    du[3] = u[1] * u[2] - p[3] * u[3]
+end # function lorenz!
+
+function lorenz_data(u0, tspan, p, dt)
+    system = ODEProblem(lorenz!, u0, tspan, p) # define ODE problem
+    times = collect((tspan[1]):dt:(tspan[2])) # constant timestamps
+
+    solve(system, DP5(), dt = dt, saveat = times) # solve with Explicit Runge-Kutta Method.
+end # function lorenz_data
+
+function lorenz_data(u0, tspan, p)
+    # define ODE system
+    system = ODEProblem(lorenz!, u0, tspan, p)
+
+    solution = solve(system, Rosenbrock23()) # solve using Tsit5
+
+    solution
+end # function lorenz_data

### 2024-04-10 Code/DynamicsRecovery/src/Systems/solve_constructed_system.jl

@@ -1,0 +1,72 @@
+using DifferentialEquations
+
+using DynamicsRecovery.Utils
+
+function solve_constructed_system(Ξ, u0, tspan; polynomials = [], functions = [], functions1 = [])
+    # add polynomials terms
+    append!(functions, construct_polynomials(polynomials, size(Ξ)[2]))
+
+    # add functions in functions1
+    for func in functions1
+        for n in 1:size(Ξ)[2]
+            # call function on the nth variable
+            f(x...) = func(x[n])
+
+            push!(functions, f)
+        end # for n
+    end # for func
+
+    # strip out only relevant functions
+    relevant_functions::Vector{Vector{Any}} = []
+    relevant_functions_coefficients::Vector{Vector{Any}} = []
+
+    for n in 1:size(Ξ)[2]
+        n_rel_funcs = []
+        n_rel_funcs_coef = []
+        
+        for i in 1:length(functions)
+            # skip if the coefficient is 0
+            if Ξ[i, n] == 0
+                continue
+            end # if 
+
+            push!(n_rel_funcs, functions[i])
+            push!(n_rel_funcs_coef, Ξ[i, n])
+        end # for i
+
+        # add zero function if no functions where added
+        if isempty(n_rel_funcs) 
+            z0(x...) = 0.0 # zero map
+            push!(n_rel_funcs, z0)
+            push!(n_rel_funcs_coef, 0.)
+        end # if
+
+
+        push!(relevant_functions, n_rel_funcs)
+        push!(relevant_functions_coefficients, n_rel_funcs_coef)
+    end # for n
+
+    dimension = size(Ξ)[2]
+
+    function found_system!(du, u, p, t)
+        evaluated_functions::Vector{Vector{Any}} = []
+
+        for n in 1:dimension 
+            eval_funcs_n = []
+
+            # evaulate each function
+            for i in eachindex(relevant_functions[n])
+                push!(eval_funcs_n, relevant_functions[n][i](u...))
+            end # for i 
+
+            push!(evaluated_functions, eval_funcs_n)
+        end # for n
+
+        for n in 1:dimension
+            du[n] = sum(evaluated_functions[n] .* relevant_functions_coefficients[n]) # multiply all functions by the coefficients and sum up all the functions
+        end # for n 
+    end # function found_system!
+
+    system = ODEProblem(found_system!, u0, tspan)
+    # solve(system, Rosenbrock23())
+end # function solve_constructed_system

### 2024-04-10 Code/DynamicsRecovery/src/Systems/utils.jl

@@ -1,0 +1,9 @@
+using Random
+using Distributions 
+
+function add_noise_to_sample(data::Vector{Vector{Float64}}, η)
+    # generate noise out of normal centered at 0 with maginutde η
+    noise::Vector{Vector{Float64}} = η .* eachrow(rand(Normal(0,1), (size(data)[1], size(data[1])[1])))
+
+    data + noise
+end # function add_noise_to_sample

### 2024-04-10 Code/DynamicsRecovery/src/Utils/Utils.jl

@@ -1,0 +1,11 @@
+module Utils
+
+export construct_polynomials
+
+include("construct_polynomial_functions.jl")
+
+export print_constructed_system
+
+include("print_constructed_system.jl")
+
+end # module Utils

### 2024-04-10 Code/DynamicsRecovery/src/Utils/construct_polynomial_functions.jl

@@ -1,0 +1,35 @@
+using Combinatorics
+
+function construct_polynomials(degrees::Vector{T}, n::S) where T <: Integer where S <: Integer
+    functions = []
+    for deg in degrees
+        # n = 0 is a special case 
+        if deg == 0
+            C(x...) = 1  # constant
+            push!(functions,
+                C
+            )
+
+            continue
+        end # if 
+        # if deg == 1 
+        #     I(x...) = [x...] # identity
+        #     push!(functions, I)
+
+        #     continue
+        # end # if
+
+        
+        # all nth degree polynomials will be all combinations with replacement of the variables 
+        nth_degree_polynomial_iter = with_replacement_combinations(collect(1:n), deg)  
+
+        for poly in nth_degree_polynomial_iter 
+            P(x...) = prod(x[poly])
+
+            push!(functions, P)
+        end # for poly
+
+    end # for n
+
+    functions
+end # function construct_polynomials

### 2024-04-10 Code/DynamicsRecovery/src/Utils/print_constructed_system.jl

@@ -1,0 +1,65 @@
+using Combinatorics
+
+function print_constructed_system(Ξ; polynomials = [], functions = [], functions1 = [])
+    n = size(Ξ)[2] # system dimension
+
+    polynomial_terms = []
+
+    for deg in polynomials
+        # n = 0 is a special case 
+        if deg == 0
+            C(x...) = 1  # constant
+            push!(functions,
+                C
+            )
+
+            continue
+        end # if 
+        # all nth degree polynomials will be all combinations with replacement of the variables 
+        nth_degree_polynomial_iter = with_replacement_combinations(collect(1:n), deg)  
+
+        # add to collection of polynomials
+        append!(polynomial_terms, collect(nth_degree_polynomial_iter))
+    end # for deg
+
+    # vector of equation strings 
+    equations = []
+
+    for k in 1:n
+        equation_str = "\\dot u_" * string(k) * " = " 
+
+        # go through functions first
+        for i in eachindex(functions)
+            # if you have a nonzero coefficient, add it 
+            if Ξ[i, k] != 0
+                equation_str *= string(Ξ[i, k]) * "f_$i + "
+            end # if 
+        end # for i 
+
+        # go through polynomials
+        for i in eachindex(polynomial_terms)
+            poly_i = i + length(functions)
+
+            if Ξ[poly_i, k] != 0 
+                poly_term = prod(["u_$j" for j in polynomial_terms[i]])
+
+                equation_str *= string(Ξ[poly_i, k]) * poly_term * " + " 
+            end # if 
+        end # for i
+
+        # go through remaining 1-parameter functions 
+        for i in eachindex(functions1)
+            func_i = length(functions) + length(polynomial_terms) + (i-1)*n
+
+            for j in 1:n
+                if Ξ[func_i + j, k] != 0
+                    equation_str *= string(Ξ[func_i + j, k]) * "g_$i(u_$j) + "
+                end # if
+            end # for j
+        end # for i
+
+        push!(equations, equation_str)
+    end # for k
+    
+    equations
+end # print_constructed_system

### 2024-04-10 Code/main_pluto.jl

@@ -1,0 +1,339 @@
+### A Pluto.jl notebook ###
+# v0.19.40
+
+using Markdown
+using InteractiveUtils
+
+# ╔═╡ 71998b4b-1bfc-4c3d-8c7e-5741de700162
+using Pkg
+
+# ╔═╡ 0e6831be-f2e1-11ee-1ecc-1f97692f0c45
+begin
+# using Pkg
+Pkg.activate("./DynamicsRecovery")
+using Revise
+using DynamicsRecovery
+end
+
+# ╔═╡ aa29b69a-5750-4a5f-8e8c-fdc49d9a45b6
+begin
+	using DifferentialEquations
+	using LinearAlgebra
+	using Statistics
+	using LaTeXStrings
+	using Combinatorics
+end
+
+# ╔═╡ 1511b58f-0ec9-4dc3-90ec-d3169cf9189e
+begin
+	# Pkg.add("PyPlot")
+	# Pkg.add("PlotlyBase")
+	
+	using Plots
+	plotly()
+	# pyplot()
+end
+
+# ╔═╡ 51281685-dea0-4c19-b6c6-893b265b051c
+begin 
+	using PlotlyKaleido
+	PlotlyKaleido.start()
+	Plots.savefig("./found_hopf_bifurcation_0005.pdf")
+end
+
+# ╔═╡ a0a26a0d-a7e9-4168-996b-51f44fd96dad
+# Pkg.add("LaTeXStrings")
+# Pkg.add("PlotlyKaleido")
+
+# ╔═╡ 61ccdc43-c12f-4b59-b746-316c82b342a5
+md"""
+# Lorenz
+
+"""
+
+# ╔═╡ f2f7d603-4836-4010-95c7-10def9254590
+begin
+
+	lorenz_system = lorenz_data([-8., 7., 27.], (0.,100.), (10., 28., 8/3), 0.001)
+	# lorenz_dt = lorenz_system.t[2] - lorenz_system.t[1]
+	lorenz_system.t
+end
+
+# ╔═╡ 4cbdb8af-68ca-421f-853c-5bd8c4f4b464
+plot(lorenz_system, idxs=(1,2,3), legend = false, xlabel = "x", ylabel = "y", zlabel = "z", camera=(40,30))
+
+# ╔═╡ b2a4fb51-90a0-49af-9a3e-f0d21a54495d
+begin
[…]

### 2024-04-21 Paper/main.tex
idek what this was

@@
 
-\section{Introduction}
-\label{sec:introduction}
-This project discusses the procedure of recovering the underlying equations for the dynamics given noisy data collected by the system. So called ``physics-inspired'' or ``physics-informed'' AI.
-The goal of this field is to gain a physical understanding of systems where we can measure various trajectories, but the dynamics are unknown.
+\section{Introduction} \label{sec:introduction}
+Dynamical systems are mathematical objects used to describe anything and everything that changes.
+This gives rise to their utility in modeling a vast array of applications.
+Of course, physical systems are of particular interest as the rules of physics work in terms of velocity and acceleration---the descriptors of movement.
+Though, in principle, far more than the cannonical examples of physical movement are ``changing.'' Economic models describe the changes in producer and consumer supply and demand, while biologists model the rise and fall of organism populations in an ecosystem.
+The prevalence of these inherently changing systems leads to the field of dynamical systems having vast applicability to the world of mathematical modeling.
+Though while they are often the natural language to describe these situations, determining the particular dynamics in a given system is a fundamentally difficult problem.
+
+This paper discusses a method through which data can be used to uncover the governing equations for a dynamical system. 
+%
+% This project discusses the procedure of recovering the underlying equations for the dynamics given noisy data collected by the system. So called ``physics-inspired'' or ``physics-informed'' AI.
+% The goal of this field is to gain a physical understanding of systems where we can measure various trajectories, but the dynamics are unknown.
 Though this is additionally useful in situations where complex systems have dynamical properties that can be modeled on a smaller scale.
-In particular, the focus of this project is on discussing the results demonstrated in a paper published in 2016 by Steven Brunton, Joshua Proctor, and Nathan Kutz who propose an algorithm for reconstructing dynamics dubbed SINDy (Sparse Identification of Nonlinear Dynamics) \cite{sindy}.
-This first section aims to discuss the field more broadly and relevant papers to the results proposed in the aforementioned paper as well as more generally in the field.
+In particular, the focus of this paper is on discussing the results demonstrated by Steven Brunton, Joshua Proctor, and Nathan Kutz in their paper published in 2016.
+They propose a new algorithm for reconstructing dynamics within a system called SINDy (Sparse Identification of Nonlinear Dynamics) \cite{sindy}.
+% This first section aims to discuss the field more broadly and relevant papers to the results proposed in the aforementioned paper as well as more generally in the field. 
+In this first section, I will discuss the field more broadly prior to Brunton, Proctor, and Kutz published their work.
+This will include a dicussion of relevant papers that provided the groundwork for the SINDy algorithm.
+In the section section (\ref{sec:mathematical_background}), I will discuss the relevant mathematical background for SINDy and its underlying mathematics.
+Section \ref{sec:results} will go deeper into the results demonstrated by Brunton et al.
+by discussing my work to recreate the SINDy algorithm.
+Finally, section \ref{sec:discussion} offers a dicussion of the results in the paper and further areas of interest.
 
 The authors of \cite{sindy} give two foundational papers for recovering the dynamics of nonlinear systems: a paper by Josh Bongard and Hod Lipson \cite{bongard} and one by Michael Schmidt and Hod Lipson \cite{schmidt}, in 2007 and 2009 respectively.
-Bongard and Lipson \cite{bongard} outline a method for ``reverse engineering'' the dynamics of nonlinear systems utilizing an active learning system. 
+Bongard and Lipson \cite{bongard} outline a method for ``reverse engineering'' the dynamics of nonlinear systems by utilizing an active learning system. 
 The main process of the algorithm is a technique labeled \textbf{symbolic regression}.
+Fundamentally, symbolic regression is a regression algorithm that is used to build up arbitrary equations to represent the given data.
+This is often accomplished through a genetic algorithm where ``function blocks'' are used to build possible functions, which are then tested with the best being used to create the next generation.
 In \cite{bongard}, symbolic regression is made usable for complicated (nonlinear) systems by introducing three concepts: partitioning, automated probing, and snipping.
-Partitioning is a process by which the algorithm is able to model each of the variables in the system separately using Stochastic optimization.
+Partitioning is a process by which the algorithm is able to model each of the variables in the system separately using stochastic optimization.
 Each of the variables are integrated by substituting in representations of the other variables rather than integrating the variables together.
@@
 In particular, when creating another generation of models, occasionally certain subexpressions will be replaced with a value of the subexpression picked uniformly from its range.
-This acts to reduce situations where the models will create complex subexpressions which take on narrow ranges of values, demonstrating over-fitting to the data.
+This process reduces situations where the model constructs complex subexpressions which take on narrow ranges of values, a hallmark of over-fitting data.
 Together, these innovations on the process of symbolic regression allowed Bongard and Lipson to create a framework that was applicable to an array of real-world systems.
@@
 
-Schmidt and Lipson present a different algorithm for reconstructing dynamics that is still based on \textbf{symbolic regression} \cite{schmidt}.
+Schmidt and Lipson present another algorithm for reconstructing dynamics, also based on \textbf{symbolic regression} \cite{schmidt}. 
 This paper focuses on presenting a new metric for comparing the accuracy of various candidate equations in order to better search for invariants within the system. 
-In particular, once candidate equations are generated (initially randomly from a set of ``building blocks''), the partial derivative pairings of every pair of variables are compared to the numerically calculated partial derivative pairings in order to select the equations which model these pairs the closest.
-The next generation of equations is then generated from these best equations probabilistically.
-The algorithm will return a set of equations when they reach a certain accuracy to the observed data, calculated from a subset of the data randomly selected to be withheld from training.
-Furthermore, these equations are prioritized according to a measured parsimony, effectively complexity which is calculated by the number of terms in the expression.
+In particular, once candidate equations are generated (initially randomly from a set of ``building blocks''), the partial derivative pairings of every pair of variables are compared to the numerically calculated
+partial derivative pairings in order to select the equations which model these pairs the closest. They generate the next generation of equations probablistically from the best equations.
+To determine the accuracy of equations on the observed data, the authors withhold a random sample from the collected data for testing and when the equations reach a certain level of accuracy, the algorithm terminates.
+Finally, equations are prioritized accoriding to measured parsimony---roughly calculated as the number of terms in the expression. 
 The authors were able to demonstrate that this algorithm could reconstruct invariants from numerous physical systems effectively.
@@
 
-\section{Mathematical Background}
+\section{Mathematical Background} \label{sec:mathematical_background}
 For the SINDy algorithm, the authors aimed to reframe the problem of recovering nonlinear dynamics using \textbf{sparse regression} and \textbf{compressed sensing} \cite{sindy}.
@@
 
-\section{Results}
+\section{Results} \label{sec:results}
 \subsection{Code}
@@
 
+\section{Discussion} \label{sec:discussion}
+
 % \section{}

### 2024-04-21 Code/DynamicsRecovery/src/DynamicsRecovery.jl

@@ -5,17 +5,18 @@ using .Utils
 export construct_polynomials
 export print_constructed_system
 
-include("SINDy/SINDy.jl")
-using .SINDy
-export constructX, Θ, sparse_regression
-export TvDiffParams
-
 include("Systems/Systems.jl")
 using .Systems
 export hopf_normal!
 export lorenz_data, lorenz!
 export add_noise_to_sample
-export solve_constructed_system
+export solve_constructed_system, get_constructed_system
+
+include("SINDy/SINDy.jl")
+using .SINDy
+export constructX, Θ, sparse_regression
+export TvDiffParams
+export active_SINDy, measure_accuracy, measure_sparsity
 
 
 end # module DynamicsRecovery

### 2024-04-21 Code/DynamicsRecovery/src/SINDy/SINDy.jl

@@ -13,5 +13,9 @@ export sparse_regression
 
 include("sparse_regression.jl")
 
+export active_SINDy, measure_accuracy, measure_sparsity
+
+include("active_algorithm.jl")
+
 end # module SINDy
 

### 2024-04-21 Code/DynamicsRecovery/src/SINDy/active_algorithm.jl

@@ -1,0 +1,104 @@
+using DifferentialEquations
+using LinearAlgebra
+using ProgressMeter
+using StatsBase
+
+using DynamicsRecovery.Systems
+
+# function λ_sparsity_fitting(λ0, X::Matrix{Float64}, Xdot::Matrix{Float64}, X_test::Matrix{Float64}, Xdot_test::Matrix{{Float64}})
+# end 
+
+"""
+    active_SINDy(system, dt, tspan0, u0, p, sol_method, η, control_param_range, tvdiff_params, λ0, kmax, desired_sparsity, λ_stepping; polynomials = [], functions = [], functions1 = [])    
+
+Assumes that last(u) is the control parameter and that the intital condition for that control parameter is in u0.
+"""
+function active_SINDy(system!, dt, tspan0, u0, p, sol_method, η, control_param_range, tvdiff_params, λ0, kmax, desired_sparsity, λ_stepping; polynomials = [], functions = [], functions1 = [])
+    # first generate initial data from initial position
+    problem_initial = ODEProblem(system!, u0, tspan0, p)
+    saveat_dt_initial = collect((tspan0[1]):dt:(tspan0[2])) # times to save data at 
+    sol_initial = solve(problem_initial, sol_method, dt = dt, saveat = saveat_dt_initial) # solve system
+
+    sol_with_noise = add_noise_to_sample(sol_initial.u, η)
+
+    # solve initial SINDy system
+    X_initial, Xdot_initial = constructX(sol_with_noise, tvdiff_params, sol_initial.t)
+
+    Xtest, Xdottest, X, Xdot = get_testing_X(X_initial, Xdot_initial, 0.3)
+
+    # TODO: pick smaller basis for initial solve ?
+
+    Θ_initial = Θ(X; polynomials = polynomials, functions = functions, functions1 = functions1)
+    Ξ_initial = sparse_regression(Θ_initial, Xdot, λ0, kmax)
+
+    λ = λ0
+    Ξ = Ξ_initial
+
+    progress_meter = ProgressThresh(desired_sparsity; desc = "Minimizing:")
+    # want to search for a reasonable sparisty parameter
+    for _ in 1:1000 # large loop, change to parameter later? 
+        Ξ_new = sparse_regression(Θ_initial, Xdot, λ + λ_stepping, kmax)
+
+        # don't want to go under threshold as that could caused problems (theoretically?)
[…]

### 2024-04-21 Code/DynamicsRecovery/src/Systems/Systems.jl

@@ -12,7 +12,7 @@ export add_noise_to_sample
 
 include("utils.jl")
 
-export solve_constructed_system
+export solve_constructed_system, get_constructed_system
 
 include("solve_constructed_system.jl")
 

### 2024-04-21 Code/DynamicsRecovery/src/Systems/solve_constructed_system.jl

@@ -3,6 +3,15 @@ using DifferentialEquations
 using DynamicsRecovery.Utils
 
 function solve_constructed_system(Ξ, u0, tspan; polynomials = [], functions = [], functions1 = [])
+
+    found_system! = get_constructed_system(Ξ; polynomials = polynomials, functions = functions, functions1 = functions1)
+
+    system = ODEProblem(found_system!, u0, tspan)
+    # solve(system, Rosenbrock23())
+end # function solve_constructed_system
+
+function get_constructed_system(Ξ; polynomials = [], functions = [], functions1 = [])
+
     # add polynomials terms
     append!(functions, construct_polynomials(polynomials, size(Ξ)[2]))
 
@@ -67,6 +76,5 @@ function solve_constructed_system(Ξ, u0, tspan; polynomials = [], functions = [
         end # for n 
     end # function found_system!
 
-    system = ODEProblem(found_system!, u0, tspan)
-    # solve(system, Rosenbrock23())
-end # function solve_constructed_system
+    found_system!
+end # function get_constructed_system

### 2024-04-21 Code/main_pluto.jl

@@ -44,6 +44,7 @@ end
 # ╔═╡ a0a26a0d-a7e9-4168-996b-51f44fd96dad
 # Pkg.add("LaTeXStrings")
 # Pkg.add("PlotlyKaleido")
+# Pkg.instantiate()
 
 # ╔═╡ 61ccdc43-c12f-4b59-b746-316c82b342a5
 md"""
@@ -288,7 +289,18 @@ end
 # end
 
 # ╔═╡ daa284d3-f9bc-45b7-9c53-df70ab60c204
+begin 
+	test = active_SINDy(lorenz!, 0.001, (0.,100.), [-8., 7., 27.], (10., 28., 8/3), Tsit5(), 0.01, (0., 100.), TvDiffParams(), 0.0001, 10, 0.98, 0.0001; polynomials = collect(0:5))
+end
 
+# ╔═╡ 9d481e6c-feef-4f85-a9ea-d7def332580d
+begin 
+	test_system = solve_constructed_system(test, [-8., 7., 27.], (0., 100.); polynomials = collect(0:5))
+	test_sol = solve(test_system, Tsit5())
+end
+
+# ╔═╡ ca23d1c7-4efd-4097-a6e4-cf6e5cd84fa5
+plot(test_sol, idxs=(1,2,3))
 
 # ╔═╡ Cell order:
 # ╠═71998b4b-1bfc-4c3d-8c7e-5741de700162
@@ -337,3 +349,5 @@ end
 # ╠═51281685-dea0-4c19-b6c6-893b265b051c
 # ╠═2df97f42-ec7f-4c6f-9431-3b69a8cb8024
 # ╠═daa284d3-f9bc-45b7-9c53-df70ab60c204
+# ╠═9d481e6c-feef-4f85-a9ea-d7def332580d
+# ╠═ca23d1c7-4efd-4097-a6e4-cf6e5cd84fa5

### 2024-04-21 Paper/main.tex
discussion section draft complete

@@
 
-\jlinputlisting[language = Julia, caption = {Lorenz system data simulation}, label = {lorenz_data}, firstline = 9, lastline = 14]{../Code/DynamicsRecovery/src/Systems/lorenz.jl}
-
 Additionally, noise sampled from a standard normal distribution was scaled by a noise parameter and added to the collected data before SINDy was trained on it.
@@
 The code for constructing the data and derivative libraries is shown in Listing \ref{X_Xdot_construction}.
-
-% https://tex.stackexchange.com/questions/73231/avoid-page-breaks-in-lstlistings
-% https://tex.stackexchange.com/questions/39017/how-to-influence-the-position-of-float-environments-like-figure-and-table-in-lat
-\jlinputlisting[language = Julia, caption = {Data and derivative library construction}, label = {X_Xdot_construction}, firstline = 68, lastline = 95, float, floatplacement = tb]{../Code/DynamicsRecovery/src/SINDy/data_ingestion.jl}
 
@@
 \begin{figure}[h]
-	\caption{Discovered Hopf bifurcation. Blue orbits start at $(x_0, y_0) = (2,0)$ and red orbits start at $(x_0, y_0) = (0.01, 0)$.}
+	\caption{Discovered Hopf bifurcation. Blue orbits have initial condition $(x_0, y_0) = (2,0)$ and red orbits have initial condition $(x_0, y_0) = (0.01, 0)$.}
 	\label{fig:discovered_hopf_0005}
@@
 	\begin{split}
-		\dot x &= -0.9971y + 0.8704\mu x - 0.8617x^3 - 0.9177xy^2 + 0.9186\mu x^2 y  - 0.2853 xy^3 \\
-		&\qquad - 0.9918 \mu x y^2 - 0.8546 x^4y + 1.2614 x^3y^2 - 1.0363 x^2y^3 + 1.0065 xy^4 \\ &\qquad + 0.5446\mu y^3 x, \\
+		\dot x &= -0.9971y + 0.8704\mu x - 0.8617x^3 - 0.9177xy^2 + 0.9186\mu x^2 y   \\
+		&\qquad - 0.2853 xy^3- 0.9918 \mu x y^2 - 0.8546 x^4y + 1.2614 x^3y^2  \\ &\qquad - 1.0363 x^2y^3 + 1.0065 xy^4+ 0.5446\mu y^3 x, \\
 		\dot y &= 0.9968x + 0.9930\mu y - 0.9807x^2y - 0.9822 y^3.
@@
 \end{equation}
-Interestingly, while $\dot y$ remained stable, $\dot x$ tends to me less stable.
+Interestingly, while $\dot y$ remained stable, $\dot x$ tends to be less stable.
 It is important to note, that while there are many additional higher-order polynomial terms, the qualatative behavior of the system is identical, still finding a Hopf bifurcation.
@@
 \section{Discussion} \label{sec:discussion}
+
+In writing a ground-up implementation of the SINDy algorithm, I was able to replicate much of the success found by Brunton et al.
+in their paper presenting SINDy \cite{sindy}.
+In particular, I was able to demonstrate
+remarkable success in replicating the qualatative behavior of both chaotic systems (Figure \ref{fig:lorenz_system_found_001}, Figure \ref{fig:lorenz_system_found_01}) and in systems with bifurcations (Figure \ref{fig:discovered_hopf_0005}).
+Further, I found that SINDy was able to successfully determine the relevant nonlinearities in some cases (Equation \ref{eq:found_lorenz_001}, Equation \ref{eq:found_lorenz_001_tv}), and in most cases determine these almost correctly (Equation \ref{eq:found_lorenz_01_tv}, Equation \ref{eq:discovered_hopf_0005}).
+In all, this demonstrates a remarkable ability for SINDy to be used to gleam insights into the underlying dynamics of a system when only time series data on the system is available.
+
+However, it is important to note that I observed run to run variability in the success of the SINDy algorithm.
+In particular, as demonstrated by the difference between Equation \ref{eq:discovered_hopf_0005} and Equation \ref{eq:bad_discovered_hopf_0005}, the stability of SINDy isn't guarnateed.
+In particular, the run-to-run difference here is in the randomly generated noise.
+Therefore, this is indicative of SINDy being reliant on particularly beneficial conditions.
+However, depending on the application, this could be reasonably ignored as the qualitative behavior of system (\ref{eq:discovered_hopf_0005}) and (\ref{eq:bad_discovered_hopf_0005}) was the same, allowing the resulting system to predict broad-strokes behavior of the system.
+
+Another condition on the performance of the SINDy algorithm is the choice of basis.
+Brunton et al.
+emphasize the necessity of a properly chosen basis in their work \cite{sindy}, and I was also able to demonstrate this sensitivity to the basis chosen.
+A deeper discussion on the instability noticed for different bases when running SINDy on the Lorenz System is noted in Appendix \ref{apx:lorenz_with_diff_bases}, however as summary, the choice of basis is not simply in exhaustion of potential function candidates, but can also cause SINDy to perform worse if the solution is too sparse in the chosen basis.
+Further, SINDy can show instability with single function additions to the basis, and fails to perform at all when the basis doesn't contain the necessary function candidates.
+
+For these reasons, exploring methods to determine good bases for SINDy is a fruitful area of further exploration, in addition to methods for automatically determining the sparsity parameter, $\lambda$.
+% REMOVE IF I DO EXPLORE THIS
+If such methods could increase the stability of SINDy, they could dramatically improve its usability.
+Without trust in the solutions produced, particularly with possible variations simply down to noise, it would be difficult to deploy SINDy to an application where the derived system would need to be trusted.
+A possible extention to address these issues could also be in the form of active learning with the SINDy algorithm.
+Fasel et al.
+propose a modification to SINDy with control in order to implement said active learning into SINDy \cite{9683120}.
+
+Despite the difficulties in the consistency of SINDy, the applications for such a system could be expansive.
+In systems where non-conventional dynamical systems may apply, an algorithm like SINDy could be used to create a guess at the underlying dynamics in order to improve projections.
+A situation such as the stock market may be an interesting area of study using SINDy, or a similar algorithm, as the dynamics of the stock market are heavily obfuscated and potentially such an algorithm could gleam useful information on the dynamics from just the data.
+Robotic applications such as surface finishing could also potentially benefit from an algorithm such as SINDy.
+In particular, the response to pressure from the end-effector on a part could have implications on the quality of the ultimate finishing job.
+If in-perfect, but generally accurate systems could be constructed to model such feedback, it could greatly improve the robot's understanding of the part and how to finish it.
 
@@
 
+\appendix 
+\newpage
+\section{Code} \label{apx:code}
+\jlinputlisting[language = Julia, caption = {Lorenz system data simulation}, label = {lorenz_data}, firstline = 9, lastline = 14]{../Code/DynamicsRecovery/src/Systems/lorenz.jl}
+
+% https://tex.stackexchange.com/questions/73231/avoid-page-breaks-in-lstlistings
+% https://tex.stackexchange.com/questions/39017/how-to-influence-the-position-of-float-environments-like-figure-and-table-in-lat $ , float, floatplacement = tb
+\jlinputlisting[language = Julia, caption = {Data and derivative library construction}, label = {X_Xdot_construction}, firstline = 68, lastline = 95]{../Code/DynamicsRecovery/src/SINDy/data_ingestion.jl}
+
+\newpage 
+\section{Lorenz System with Different Bases} \label{apx:lorenz_with_diff_bases}
+It is important to illustrate the sensitivity of the SINDy algorithm on the chosen basis. For the Lorenz System, performance was strong for bases that included a sufficient array of polynomials. 
+In Figures \ref{fig:found_lorenz_ex_1}, \ref{fig:found_lorenz_ex_2}, \ref{fig:found_lorenz_ex_3}, and \ref{fig:found_lorenz_ex_4} we see the performance of SINDy with a bases comprised of only polynomials.
+All examples are using the same $\mathbf X$ and $\mathbf {\dot X}$ matrices, with noise $\eta = 0.1$, and using the total-variation regularization derivative.
+We see that when the basis is composed of polynomials up to seventh-degree, the identified system (\ref{eq:discovered_lorenz_ex_1}) has correctly identified the basis components with the exception of including a forcing term in $\dot z$.
+When including polynomials through fifth-degree, SINDy is able to identify only the correct basis components in the identified system (\ref{eq:discovered_lorenz_ex_2}). 
+Up to third-degree, the performance deteriorates significantly for $\dot z$, including a forcing term in $\dot z$ and including an $x^2$ term instead of a $z$ term (\ref{eq:discovered_lorenz_ex_3}).  
+Finally, when only including up to second-degree polynomials, the minimum number required to model the Lorenz System, SINDy is able to correctly identify $\dot x$ and $\dot z$, but fails to include the $y$ term in $\dot y$ (\ref{eq:discovered_lorenz_ex_4}).
+
+\begin{figure}[H]
+	\caption{Discovered Lorenz System with basis consisting of all polynomial nonlinearities up to 7th degree. Found system shown in Equation \ref{eq:discovered_lorenz_ex_1}.}
+	\label{fig:found_lorenz_ex_1}
+
+	\centering 
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{lorenz_found_basis_ex_1.pdf}
+
+	\begin{equation}\label{eq:discovered_lorenz_ex_1}
+		\begin{split}
+			\dot x &= -9.8022x + 9.8345y \\ 
+			\dot y &= 25.9081x -0.4297y -0.9457xz \\
+			\dot z &= -1.8995 -2.5435z + 0.9832xy
+		\end{split}
+	\end{equation}
+\end{figure}
+\begin{figure}[H]
+	\caption{Discovered Lorenz System with basis consisting of all polynomial nonlinearities up to 5th degree. Found system shown in Equation \ref{eq:discovered_lorenz_ex_2}.}
+	\label{fig:found_lorenz_ex_2}
+
+	\centering 
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{lorenz_found_basis_ex_2.pdf}
+
+	\begin{equation}\label{eq:discovered_lorenz_ex_2}
+		\begin{split}
+			\dot x &= -9.8022x + 9.8345y \\ 
+			\dot y &= 25.9081x  -0.4297y  -0.9457xz \\
+			\dot z &= -2.6146z + 0.9832xy
+		\end{split}
+	\end{equation}
+\end{figure}
+\begin{figure}[H]
+	\caption{Discovered Lorenz System with basis consisting of all polynomial nonlinearities up to 3th degree. Found system shown in Equation \ref{eq:discovered_lorenz_ex_3}.}
+	\label{fig:found_lorenz_ex_3}
+
+	\centering 
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{lorenz_found_basis_ex_3.pdf}
+
+	\begin{equation}\label{eq:discovered_lorenz_ex_3}
+		\begin{split}
+			\dot x &= -9.8022x + 9.8345y \\ 
+			\dot y &= 25.9081x  -0.4297y  -0.9457xz \\
+			\dot z &= -49.6281 -0.4837x^2 + 1.2756xy
+		\end{split}
+	\end{equation}
+\end{figure}
+\begin{figure}[H]
+	\caption{Discovered Lorenz System with basis consisting of all polynomial nonlinearities up to 2th degree. Found system shown in Equation \ref{eq:discovered_lorenz_ex_4}.}
+	\label{fig:found_lorenz_ex_4}
+
+	\centering 
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{lorenz_found_basis_ex_4.pdf}
+
+	\begin{equation}\label{eq:discovered_lorenz_ex_4}
+		\begin{split}
+			\dot x &= -9.8022x + 9.8345y \\ 
+			\dot y &= 24.8441x  -0.9247xz \\
+			\dot z &= -2.6146z + 0.9832xy
+		\end{split}
+	\end{equation}
+\end{figure}
+
+In two separate tests including exponentials in the function basis (i.e.
+$e^x$, $e^y$, and $e^z$), SINDy identified the zero map exclusively.
+This could be due to the sparsity parameter, $\lambda$, being too large for the application, but as a comparison to the other bases tested, $\lambda$ was held constant.
+This demonstrates some of the inconsistencies present in basis selection.
+In particular, the only chosen basis which was able to correctly identify the specific basis elements for the sysem was a basis consisting of only polynomials up to fifth-degree.
+This is particularly interesting as including sixth and seventh degree polynomials decreased the performance of SINDy.
+Additionally, while it may be expected, including sines and cosines, as with (\ref{eq:found_lorenz_01_tv}), we still found the inclusion of a forcing term in $\dot z$.
+Further, an inability to identify a system at all when adding exponentials (to bases that worked previously to identify qualitatively similar systems) demonstrates a concerning instability with only small changes in the chosen basis.
+However, it is important to note that when a sufficient quantity of polynomial basis elements are included, and with or without sines and cosines, SINDy is able to perform admirably in constructing systems with similar qualitative behavior to the Lorenz System.
+
+For completeness, when running SINDy with a basis that doesn't include any of the relevant terms, it is unable to identify a reasonable system.
+In particular, running SINDy with bases of only sines and cosines on the Lorenz System results in synthesized behavior completely distinct from the Lorenz System,
+as seen in Figure \ref{fig:found_lorenz_ex_7} and Figure \ref{fig:found_lorenz_ex_8}.
+\begin{figure}[H]
+	\caption{Discovered Lorenz System with basis $\mathcal B = \{ \sin{ku_i}, \cos{ku_i} \ | \ k \in 1, \ldots, 10, u_i \in \{x,y,z\} \}$.}
+	\label{fig:found_lorenz_ex_7}
+
+	\centering 
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{lorenz_found_basis_ex_7.pdf}
+
+\end{figure}
+\begin{figure}[H]
+	\caption{Discovered Lorenz System with basis $\mathcal B = \{ \sin{ku_i}, \cos{ku_i} \ | \ k \in 1, \ldots, 50, u_i \in \{x,y,z\} \}$.}
+	\label{fig:found_lorenz_ex_8}
+
+	\centering 
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{lorenz_found_basis_ex_8.pdf}
+
+\end{figure}
+
 \newpage

### 2024-04-21 Code/main_pluto.jl

@@ -279,6 +279,178 @@ begin
 	
 end
 
+# ╔═╡ c65722a9-d01e-4471-9c2c-e38f94dec6fc
+md"""
+# Stability testing
+"""
+
+# ╔═╡ de88e9ef-3f97-4285-9949-12c2a6481bcd
+begin
+	lorenz_polys_1 = collect(0:7)
+	lorenz_polys_2 = collect(0:5)
+	lorenz_polys_3 = collect(0:3)
+	lorenz_polys_4 = collect(0:2)
+	lorenz_polys_5 = collect(0:7)
+	lorenz_polys_6 = collect(0:7)
+	lorenz_func1_1 = []
+	lorenz_func1_2 = []
+	lorenz_func1_3 = []
+	lorenz_func1_4 = []
+	lorenz_func1_5 = [sin_cos_function_library(10)..., exp]
+	lorenz_func1_6 = [exp]
+	
+	Θ_lorenz_01_tv_1 = Θ(X_lorenz_01_tv; polynomials=lorenz_polys_1)
+	Θ_lorenz_01_tv_2 = Θ(X_lorenz_01_tv; polynomials=lorenz_polys_2)
+	Θ_lorenz_01_tv_3 = Θ(X_lorenz_01_tv; polynomials=lorenz_polys_3)
+	Θ_lorenz_01_tv_4 = Θ(X_lorenz_01_tv; polynomials=lorenz_polys_4)
+	Θ_lorenz_01_tv_5 = Θ(X_lorenz_01_tv; polynomials=lorenz_polys_5, functions1 = lorenz_func1_5)
+	Θ_lorenz_01_tv_6 = Θ(X_lorenz_01_tv; polynomials=lorenz_polys_6, functions1 = lorenz_func1_6)
+end
+
+# ╔═╡ b1636e3d-14c9-423c-8425-1cdd4ec5ce3f
+begin 
+	lorenz_polys_7 = [0]
+	lorenz_polys_8 = [0]
+	lorenz_polys_9 = [0]
+	
+	lorenz_func1_7 = [sin_cos_function_library(10)...]
+	lorenz_func1_8 = [sin_cos_function_library(50)...]
+	lorenz_func1_9 = [sin_cos_function_library(100)...]
+
[…]

### 2024-04-24 Code/DynamicsRecovery/src/DynamicsRecovery.jl
presentation!

@@ -16,7 +16,7 @@ include("SINDy/SINDy.jl")
 using .SINDy
 export constructX, Θ, sparse_regression
 export TvDiffParams
-export active_SINDy, measure_accuracy, measure_sparsity
+export active_SINDy, measure_accuracy, measure_sparsity, get_testing_X
 
 
 end # module DynamicsRecovery

### 2024-04-24 Code/DynamicsRecovery/src/SINDy/SINDy.jl

@@ -13,7 +13,7 @@ export sparse_regression
 
 include("sparse_regression.jl")
 
-export active_SINDy, measure_accuracy, measure_sparsity
+export active_SINDy, measure_accuracy, measure_sparsity, get_testing_X
 
 include("active_algorithm.jl")
 

### 2024-04-24 Code/DynamicsRecovery/src/SINDy/active_algorithm.jl

@@ -66,17 +66,25 @@ end # function measure_sparsity
 function measure_accuracy(Ξ, testX::Matrix{Float64}, testXdot::Matrix{Float64}; polynomials =[], functions = [], functions1 = [])
     system! = get_constructed_system(Ξ; polynomials = polynomials, functions = functions, functions1 = functions1)
 
-    total_difference = 0.
+    total_difference = BigFloat.(zeros(size(testXdot)[2]))
+
+    total_derivative = BigFloat.(zeros(size(testXdot)[2]))
 
     for (x, xdot) ∈ zip(eachrow(testX), eachrow(testXdot))
         du = zeros(size(xdot))
 
         system!(du, x, (0.), 0.) # zeros are nothing
 
-        total_difference += norm(xdot - du)^2 
+        total_difference += (xdot - du).^2
+        total_derivative += xdot
     end # for
 
-    sqrt(total_difference)/size(testXdot)[1]
+    total_derivative = map(x -> x == 0. ? 1 : x, total_derivative) # edge case when derivatives are all 0
+
+    average_diff = (total_difference ./ size(testXdot)[1] ) ./ total_derivative
+
+    norm(average_diff)
+    # (sqrt(total_difference)/size(testXdot)[1]) / norm(average)
 end # function measure_accuracy
 
 function get_testing_X(X::Matrix{Float64}, Xdot::Matrix{Float64}, a::Float64)

### 2024-04-24 Code/main_pluto.jl

@@ -30,21 +30,62 @@ begin
 	# Pkg.add("PlotlyBase")
 	
 	using Plots
-	plotly()
+	gr()
 	# pyplot()
 end
 
-# ╔═╡ 51281685-dea0-4c19-b6c6-893b265b051c
+# ╔═╡ ee6d98bc-97dc-48f4-92fe-79a69afd51ca
+begin
+using Colors
+
+function expand_palette(bg, cs; kwargs...)
+    colors = palette(cs).colors.colors
+    c = convert.(RGBA, distinguishable_colors(20, vcat(bg, colors); kwargs...))[2:end]
+    return palette(c)
+end
+end
+
+# ╔═╡ e4a6e6f9-43c6-489e-9ae2-451ee1f9e0df
 begin 
 	using PlotlyKaleido
 	PlotlyKaleido.start()
-	Plots.savefig("./found_hopf_bifurcation_0005.pdf")
 end
 
 # ╔═╡ a0a26a0d-a7e9-4168-996b-51f44fd96dad
 # Pkg.add("LaTeXStrings")
 # Pkg.add("PlotlyKaleido")
 # Pkg.instantiate()
+
+# ╔═╡ f7fb3eaf-0473-4074-a99c-892655fe12b7
+begin
+#inspired by nucleus theme for Atom
+const dark_palette = [
+    colorant"#FE4365", # red
+    colorant"#eca25c", # orange
+    colorant"#3f9778", # green
+    colorant"#005D7F" # blue
+]
+const dark_bg = colorant"#000000"
+
+const custom_theme = PlotTheme(Dict([
+    :bg => dark_bg,
+    :bginside => colorant"#000000",
+    :fg => colorant"#ADB2B7",
+    :fgtext => colorant"#FFFFFF",
+    :fgguide => colorant"#FFFFFF",
+    :fglegend => colorant"#FFFFFF",
+    :legendfontcolor => colorant"#FFFFFF",
+    :legendtitlefontcolor => colorant"#FFFFFF",
+    :titlefontcolor => colorant"#FFFFFF",
+    :palette => expand_palette(dark_bg, dark_palette; lchoices = [57], cchoices = [100]),
+    :colorgradient => :fire])
+)
+
+add_theme(:custom, custom_theme)
+end
+
[…]

### 2024-04-30 Paper/main.tex
final (maybe?) paper

--- 2024-04-21 Paper/main.tex
@@
 Dynamical systems are mathematical objects used to describe anything and everything that changes.
-This gives rise to their utility in modeling a vast array of applications.
+This gives rise to their utility in modeling a vast array of real-world systems.
 Of course, physical systems are of particular interest as the rules of physics work in terms of velocity and acceleration---the descriptors of movement.
@@
 % This first section aims to discuss the field more broadly and relevant papers to the results proposed in the aforementioned paper as well as more generally in the field. 
-In this first section, I will discuss the field more broadly prior to Brunton, Proctor, and Kutz published their work.
+In this first section, I will discuss the field more broadly prior to Brunton, Proctor, and Kutz publishing their work.
 This will include a dicussion of relevant papers that provided the groundwork for the SINDy algorithm.
-In the section section (\ref{sec:mathematical_background}), I will discuss the relevant mathematical background for SINDy and its underlying mathematics.
+I will then go on to describe relevant mathematical background for SINDy and its underlying mathematics (Section \ref{sec:mathematical_background}).
 Section \ref{sec:results} will go deeper into the results demonstrated by Brunton et al.
-by discussing my work to recreate the SINDy algorithm.
+by discussing my work to recreate the SINDy algorithm as well as further exploration into the performance of SINDy.
 Finally, section \ref{sec:discussion} offers a dicussion of the results in the paper and further areas of interest.
@@
 For the SINDy algorithm, the authors aimed to reframe the problem of recovering nonlinear dynamics using \textbf{sparse regression} and \textbf{compressed sensing} \cite{sindy}.
-Both sparse regression and compressed sensing broadly refer to the process of finding a regression solution to a problem such that the solution is sparse in some space \cite{sindy}.
+Both sparse regression and compressed sensing broadly refer to the process of finding a regression solution to a problem such that the solution is sparse in some function space \cite{sindy}.
 Brunton et al.
@@
 % mention LASSO here as alternative method for sparse regression
-The authors of \cite{sindy} propose an iterative algorithm for sparse regression.
+% The authors of \cite{sindy} propose an iterative algorithm for sparse regression.
 In particular, they start with a least-squares fit to the data, and then iteratively remove coefficients below a given threshold.
@@
 The SINDy algorithm relies on the availability of both sampled data, $\mathbf X$, and the sampled derivative, $\mathbf{\dot X}$.
-However, the authors note that the availability of derivative measurements are not guaranteed and therefore propose using the \textbf{total variation regularized derivative} to mitigate the noise created from numerically calculating $\mathbf {\dot X}$ from $\mathbf X$ \cite{sindy}.
-In particular, they cite the algorithm used by Rudin et al.
+However, the authors note that the availability of derivative measurements are not guaranteed and therefore propose using the \textbf{total-variation regularized derivative} to mitigate the noise created from numerically calculating $\mathbf {\dot X}$ from $\mathbf X$ \cite{sindy}.
+In particular, the total-variation regularization technique is attributed to Rudin et al.
 \cite{rudin}.
-Here, Rudin et al.
+This method for computing derivatives is robust to noise present in a system, without affect the performance in identifying jump discontinuities \cite{chartrand2011numerical}.
+The implementation of the total-variation regularization derivative is beyond the scope of the paper. 
+% Here, Rudin et al.
 use a framework for computing a desired, denoised output, $u$, from a noisy input, $u_0$, by assuming that $u = u_0 + n$ for some white noise function $n$.
 It is assumed that $n$ has a mean of $0$ with some given standard deviation.
-The minmization problem corresponds to minimizing $\int_\Omega \sqrt{u_x^2 + u_y^2} \, \mathrm d A$, which is contrained by $\int_\Omega u \, \mathrm dA = \int_\Omega u_0 \, \mathrm dA$ under the assumption of the additive white noise.
+% The minmization problem corresponds to minimizing $\int_\Omega \sqrt{u_x^2 + u_y^2} \, \mathrm d A$, which is contrained by $\int_\Omega u \, \mathrm dA = \int_\Omega u_0 \, \mathrm dA$ under the assumption of the additive white noise.
 It is then proposed to solve for $u$ through either an iterative algorithm (i.e.
@@
 \subsection{SINDy} \label{sec:SINDy}
-The most basic systems considered for the algorithm SINDy are those of the form 
-\[ \frac{\mathrm d}{\mathrm dt} \mathbf x(t) = \mathbf f (\mathbf x(t)). \]
-In order to use the concepts of sparse regression and compressed sensing, discussed above, the authors assume that $\mathbf f$ is sparse in some function space \cite{sindy}.
-The state vector, $\mathbf x(t)$, is collected over some time period and $\mathbf {\dot x}$ is either sampled alongside $\mathbf x(t)$ or numerically calculated from it. 
-These samplings create the following matrices: 
+The main purpose of SINDy is in identifying the function $\mathbf f$ in (\ref{eq:dynamical_system}). 
+\begin{equation}\label{eq:dynamical_system}
+	\frac{\mathrm d}{\mathrm dt} \mathbf x(t) = \mathbf f (\mathbf x(t)).
+\end{equation}
+Such identification requires the collection of timeseries data, $\mathbf X$. The form of $\mathbf X$ is as follows:
+
+% In order to use the concepts of sparse regression and compressed sensing, discussed above, the authors assume that $\mathbf f$ is sparse in some function space \cite{sindy}.
+% The state vector, $\mathbf x(t)$, is collected over some time period and $\mathbf {\dot x}$ is either sampled alongside $\mathbf x(t)$ or numerically calculated from it. 
+% These samplings create the following matrices: 
 \[ \mathbf X = \begin{bmatrix}
@@
 \end{bmatrix}, \]  
-and the immediately following $\mathbf {\dot X}$. We can then construct a library of candidate functions: 
+where each row of $\mathbf X$ is some measurement in time of the $n$ state variables in our system.
+Hence, the columns of $\mathbf X$ correspond to the different state variables of our system, and the rows of $\mathbf X$ represent timeseries data measurements from our system.
+Either sampled alongside $\mathbf X$, or numerically computed from it, we also need the relevant derivatives,
+\[ \mathbf {\dot X} = \begin{bmatrix}
+	\mathbf {\dot x}^T(t_1) \\ \mathbf {\dot x}^T(t_2) \\ \vdots \\ \mathbf {\dot x}^T(t_m)
+\end{bmatrix} = \begin{bmatrix}
+	\dot x_1(t_1) & \dot x_2(t_1) & \cdots & \dot x_n(t_1) \\
+	\dot x_1(t_2) & \dot x_2(t_2) & \cdots & \dot x_n(t_2) \\
+	\vdots & \vdots & \ddots & \vdots \\ 
+	\dot x_1(t_m) & \dot x_2(t_m) & \cdots & \dot x_n(t_m)
+\end{bmatrix}. \]  
+As discussed above, Brunton et al. propose using the total-variation regularization derivative to combat noise if numerically calculating $\mathbf {\dot X}$ from $\mathbf X$. 
+It is important to note that no assumptions are made about the time steps between each $t_i$, nor do all collected data points need to be from the same orbit.
+
+In order to specify the particular function basis we aim to use for SINDy, we construct a function library.
+In essence, this library is constructed such that each column is representative of a candidate function in our function basis,
+\[ \Theta(\mathbf X) = \begin{bmatrix}
+	g_1(\mathbf x(t_1)) & g_2(\mathbf x(t_1)) & \cdots & g_k(\mathbf x(t_1)) \\ 
+	g_1(\mathbf x(t_2)) & g_2(\mathbf x(t_2)) & \cdots & g_k(\mathbf x(t_2)) \\ 
+	\vdots & \vdots & \ddots & \vdots \\ 
+	g_1(\mathbf x(t_m)) & g_2(\mathbf x(t_m)) & \cdots & g_k(\mathbf x(t_m)) 
+\end{bmatrix}. \]
+In principle, each $g_i$ could be any function in terms of any subset of the state variables.
+Computation of $\Theta(\mathbf X)$ simply amounts to the evaluation of these candidate functions on all timeseries measurements from our system.
+We will seek a solution for the governing equation of each state variable as some linear combination of these candidate functions, 
+\[ \dot x_i(t) = \xi_{i, 1}g_1(\mathbf x(t)) + \xi_{i, 2}g_2(\mathbf x(t)) + \cdots + \xi_{i, k}g_k(\mathbf x(t)). \]
+In particular, we seek a sparse solution, meaning that most of the coefficients are zero (most $\xi_{i, j} = 0$). 
+In practice, our function library could contain a mixture of polynomial terms and sines or cosines,
+
 \[  \Theta(\mathbf X) = \begin{bmatrix} \mid & \mid & \mid & \mid &  & \mid & \mid & \\ 1 & \mathbf X & {\mathbf X}^{P_2} & {\mathbf X}^{P_3} & \cdots & \sin{(\mathbf X)} & \cos{(\mathbf X)} & \cdots \\ \mid & \mid & \mid & \mid & & \mid & \mid & \end{bmatrix}.
 \]
-Here, $\mathbf X^{P_2}$ represents the quadratic nonlinearities in $\mathbf f$, in particular: 
+Here, $\mathbf X^{P_2}$ represents the quadratic nonlinearities in $\mathbf f$, 
 \[ \mathbf X^{P_2} = \begin{bmatrix}
@@
 	x_1^2(t_m) & x_1(t_m)x_2(t_m) & \cdots & x_1(t_m)x_n(t_m) & x_2^2(t_m) & \cdots & x_n^2(t_m) \\
-\end{bmatrix}. \]
-Similarly, $\sin{(\mathbf X)}$ would be 
+\end{bmatrix}, \]
+while $\sin{(\mathbf X)}$ would be 
 \[ \sin{(\mathbf X)} = \begin{bmatrix}
@@
 \end{bmatrix}. \]
-Therefore, each column of $\Theta(\mathbf X)$ represents a candidate function for $\mathbf f$. From this, we set up the sparse regression problem
+After constructing our function library, we may continue by solving the sparse regression problem, 
 \[ \mathbf {\dot X} = \Theta(\mathbf X)\mathbf \Xi. \]
-In particular, $\mathbf \Xi = \begin{bmatrix}
+In particular, we aim to find a $\mathbf \Xi$, similar to a traditional least-squares regression, such that $\mathbf \Xi$ is sparse. 
+A further discussion of the mechanisms for performing this sparse regression are discussed in Section \ref{sec:code}. 
+We note that $\mathbf \Xi = \begin{bmatrix}
 	\boldsymbol \xi_1 & \boldsymbol \xi_2 & \cdots & \boldsymbol \xi_n
-\end{bmatrix}$ where each $\boldsymbol \xi_i$ is a sparse vector dictating which functions in the function library are active for each of the row equations in $\mathbf f$.
-The sparse regression problem is an iterative algorithm that iteratively thresholds out coefficients in $\mathbf \Xi$ under some sparsity parameter, $\lambda$, and then refits the problem on the remaining functions.
+\end{bmatrix}$ where each $\boldsymbol \xi_i$ is a sparse vector dictating the coefficients on the candidate functions for the governing equation of state variable $x_i$.
 
-The authors additionally suggest a slight modification to the algorithm in order to detect bifurcations present in a system.
-In particular, the authors appended the bifurcation parameter to the dynamics:
+The authors additionally suggest an alteration to the algorithm in order to detect bifurcations present in a system. In particular, the authors appended the bifurcation parameter to the dynamics: 
 \begin{equation} \label{eq:sindy_with_bifurcation}
@@
 Then, by sampling data from different values of $\mu$, it is possible for SINDy to reconstruct the system from combinations of $\mathbf x$ as well as $\mu$. 
-In turn, the system can then find the dynamics present with changes in $\mu$, and hence bifurcations.
+This results in an identified system that can capture the bifurcation behavior in changes of $\mu$.
 
 \section{Results} \label{sec:results}
-\subsection{Code}
-The main object in recreating the results presenting in the paper was writing a codebase that is able to recreate the SINDy algorithm. 
-I wrote the code in the Julia Programming Language \cite{julia} and with all plotting done in PlotlyBase.jl \cite{PlotlyBase.jl}.
+\subsection{Code} \label{sec:code}
+Central to recreating the results presented by Brunton et al. was writing a novel implementation of the SINDy algorithm.
+I wrote the code in the Julia Programming Language \cite{julia}.
+All data used to train the SINDy model was collected by integrating using ordinary differential equation (ODE) solvers provided by the DifferentialEquations.jl \cite{rackauckas2017differentialequations} package.
 
-All data used to train the SINDy model was collected by integrating using ordinary differential equation (ODE) solvers provided by the DifferentialEquations.jl \cite{rackauckas2017differentialequations} package.
-For the numerical stability of the model, data was collected at fixed timesteps, as shown in Listing \ref{lorenz_data} for the Lorenz system.
-
-\jlinputlisting[language = Julia, caption = {Lorenz system data simulation}, label = {lorenz_data}, firstline = 9, lastline = 14]{../Code/DynamicsRecovery/src/Systems/lorenz.jl}
-
-Additionally, noise sampled from a standard normal distribution was scaled by a noise parameter and added to the collected data before SINDy was trained on it.
-This code utilized the Distributions.jl \cite{JSSv098i16}\cite{Distributions.jl-2019} package to provide the normal distribution.
-Once the data was collected and noise applied, the program constructed the data matrix, $\mathbf X$, and the corresponding derivative matrix, $\mathbf {\dot X}$.
-Differentiation is done in one of two ways, either through direct numerical differentiation, using Interpolations.jl \cite{Interpolations.jl}, or using the total-variation regularization derivative, provided by NoiseRobustDifferentiation.jl \cite{chartrand2011numerical}\cite{NoiseRobustDifferentiation.jl}.
-Using a linear interpolation to compute the derivatives had the additional benefit of being more stable when samples were not taken with constant timestamps, and deviates in approach from the code written by Brunton et al.
-\cite{sindy}.
-The code for constructing the data and derivative libraries is shown in Listing \ref{X_Xdot_construction}.
-
-% https://tex.stackexchange.com/questions/73231/avoid-page-breaks-in-lstlistings
-% https://tex.stackexchange.com/questions/39017/how-to-influence-the-position-of-float-environments-like-figure-and-table-in-lat
-\jlinputlisting[language = Julia, caption = {Data and derivative library construction}, label = {X_Xdot_construction}, firstline = 68, lastline = 95, float, floatplacement = tb]{../Code/DynamicsRecovery/src/SINDy/data_ingestion.jl}
+In order to replicate sensor noise, randomly sampled noise from a standard normal distribution was added to all collected data ($\mathbf X$).
+This noise was scaled by some noise mangitude, $\eta$, in order to test the performance of SINDy at various levels of system noise.
+Additionally, all derivatives $(\mathbf {\dot X}$) were numerically calculated from the data after noise was applied.
+Distributions.jl \cite{JSSv098i16}\cite{Distributions.jl-2019} was used to sample the noise and NoiseRobustDifferentiation.jl \cite{chartrand2011numerical}\cite{NoiseRobustDifferentiation.jl} provided an implementation of the total-variation regularization derivative in order to compute $\mathbf{\dot X}$.
 
@@
 \cite{sindy}.
-In particular, the starting point for the iterative algorithm is a least-squares solution to the problem using a standard regression.
-Then, over $k$ iterations, coefficients in $\mathbf \Xi$ which are less than the sparsity parameter, $\lambda$, are dropped and replaced with zero.
-In each of these iterations, the regression is then recomputed with only the nonzero entries.
-This code is presented in Listing \ref{sparse_regression}.
+The code for this algorithm is shown in Listing \ref{lst:sparse_regression}.
+In particular, the algorithm starts by taking an initial ordinary least squares solution for $\mathbf \Xi$.
+Following this, the algorithm iteratively finds and removes coefficients in $\mathbf \Xi$ under some sparsity parameter, $\lambda$.
+On each iteration, after finding these small coefficients, we set these coefficients to zero and re-regress on only the remaining non-zero terms.
+Brunton et al. found that this algorithm converges rapidly (for a few iteration steps), meaning that 5-10 iterations are often sufficient.
 
-\jlinputlisting[language = Julia, caption = {Sparse regression}, label = {sparse_regression}, firstline = 3, lastline = 23, float, floatplacement = ptb]{../Code/DynamicsRecovery/src/SINDy/sparse_regression.jl}
+% \jlinputlisting[language = Julia, caption = {Sparse regression}, label = {sparse_regression}, firstline = 3, lastline = 23, float, floatplacement = ptb]{../Code/DynamicsRecovery/src/SINDy/sparse_regression.jl}
+\begin{jllisting}[language = Julia, caption = {Sparse regression}, label = {lst:sparse_regression}, float, floatplacement = ptb]
+function sparse_regression(Θ::Matrix{Float64}, Xdot::Matrix{Float64}, λ::Float64, kmax::Integer) 
+    # create initial guess for Xi as just regression
+    Ξ = Θ\Xdot
 
-The resulting system defined by $\mathbf \Xi$ can then be solved using the same methods as when collecting data for the original system.
+    for _ in 1:kmax 
+        # find coefficients that are less than λ 
+        small_coefficients = abs.(Ξ) .< λ
+
+        # set small coefficients to 0 
+        Ξ[small_coefficients] .= 0
+
+        # now individually run regression on non-zero coefficients
+        for n in 1:(size(Xdot)[2]) # loop through all state dimensions 
+            nonsmall = .!small_coefficients[:, n]
+
+            Ξ[nonsmall, n] = Θ[:, nonsmall]\Xdot[:, n]
+        end # for n
+    end # for k
+
+    Ξ
+end # function sparse_regression
+\end{jllisting}
+After this process, $\mathbf \Xi$ defines a ``discovered system'' from the data. In particular, we can use this discovered system to project dynamics for the original system.
+
+% The resulting system defined by $\mathbf \Xi$ can then be solved using the same methods as when collecting data for the original system.
 The governing equations are constructed using the same function generation from the library construction in order to ensure complete generality.
+
+\subsection{Measuring Error} \label{sec:measuring_error}
+In order to discuss the performance of SINDy, I aim to propose an error metric that accounts for the overall scale of the system, as well as a desire to improve the accuracy of the derivative over that of the orbit.
+A particular case study for the importance of emphasizing derivative accuracy over orbit accuracy is that of a chaotic system, where it would be reasonable to expect large deviations in orbits with derived systems closely matching the actual, underlying system.
+Therefore, qualitatively similar behavior could be labeled as inaccurate due to expected deviations from small variations in parameters.
+Further, we want an error metric to be proportional to the overall scale of the system, as scaling the coordinate system shouldn't change the accuracy of the derived system.
+For fulfilling these requirements, the following error metric may be used: 
+\[ \varepsilon = \sqrt{ \left( \sum_{i \in T} \frac{(\dot x_1(t_i) - f_1(t_i))^2}{\sum_{i \in T} (\dot x_1(t_i))^2} \right)^2 + \cdots + \left( \sum_{i \in T} \frac{(\dot x_n(t_i) - f_n(t_i))^2}{\sum_{i \in T} (\dot x_n(t_i))^2} \right)^2 }, \]
+where $T$ is a set of indices for the collected timeseries data, $\dot x_j(t_i)$ is the measured derivative from the system for state variable $j$ and time $i$, $f_j(t_i)$ is the same but for the found sytem, and $n$ is the state dimension.
+Typically, cross-validation techniques are used to test the accuracy of a fit, where a certain proportion of the collected data is withheld in order to calculate this error.
+Hence, $T$ represents that subset of data withheld for testing.
+In particular, this error metric can be thought of as how large, in proportion to the magnitude of the derivative of the system, the error in the derivative is for the found system.
+Throughout this paper I will cite this error metric for found systems to give an idea of the relative performance of SINDy between cases.
+As a standard, error will be calculated on 10 percent of the data randomly selected to be withheld for testing.
 
@@
 	\centering
-	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{lorenz_actual_graph.png}
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.6cm, 4.3cm, 2.5cm}, clip]{lorenz_attractor.pdf}
 \end{figure}
 
-I ran the SINDy algorithm on both data with noise of magnitude $\eta = 0.01$ and $\eta = 0.1$.
-Of interest is the system with $\eta = 0.1$ was only able to converge on a solution when the derivative was computed using the total-variation regularization derivative.
-For a function basis, I chose a basis comprised of all 7th-degree polynomial terms and all sines and cosines of the form $\sin{(ku_i)}$ and $\cos{(ku_i)}$ for all $\{u_i\} = \{x,y,z\}$ and integer $k$ from $1$ to $10$.
-This created a basis of $180$ possible functions.
-Further, the sparsification parameter was chosen to be $\lambda = 0.25$ with 10 iterations for sparse regression.
-Integration of the input data was done over a timespan from $0$ to $100$ with $dt = 0.001$. 
-The resulting systems from $\eta = 0.01$ are shown in Figure \ref{fig:lorenz_system_found_001} and the system resulting from $\eta = 0.1$ is shown in Figure \ref{fig:lorenz_system_found_01}.
-
+In this section, I will examine the performance of the SINDy algorithm across different magnitudes of noise applied to sampled points from the system. 
+In particular, I will demonstrate results for noise magnitudes $\eta = 0.01$, $\eta = 0.1$, and $\eta = 1$ where noise is generated by sampling from a standard normal distribution, and scaling the sampled noise by $\eta$.
+Further, it is important to note that noise is applied to the data matrix, $\mathbf X$, before the derivatives, $\mathbf {\dot X}$ is computed. 
+The derivatives are computed numerically from the sampled data after noise application, so in order to counteract the noise in the data, derivatives are calculated using the total-variation regularization derivative, as suggested by Brunton et al.
+\cite{sindy}.
+Data was collected with a timespan from $0$ to $100$, with $dt = 0.001$. For measuring error, $10\%$ of the collected data was withheld as testing data to compare against. 
+The results for the different levels of noise can be seen in Figure \ref{fig:found_lorenz_systems}.
 \begin{figure}[h]
-	\caption{Discovered Lorenz system with noise $\eta = 0.01$}
-	\label{fig:lorenz_system_found_001}
+	\caption{Discovered Lorenz systems with noise magnitudes $\eta = 0.01$, $\eta = 0.1$, and $\eta = 1$. Error ($\varepsilon$) is reported as described in Section \ref{sec:measuring_error}.}
+	\label{fig:found_lorenz_systems}
 
 	\centering 
-	\begin{minipage}{0.47\textwidth}
+	\begin{minipage}{0.32\textwidth}
+		\[ \eta = 0.01, \, \lambda = 0.25, \]
+		\[ \varepsilon = 0.00041 \]
 		\begin{center}
-			\includegraphics[width = \textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{lorenz_found_001_normal.png}
-
-			With standard derivative calculation
+			\includegraphics[width = 0.95\textwidth, trim={4.3cm, 1.6cm, 4.3cm, 2.5cm}, clip]{found_lorenz_001.pdf}
 		\end{center}
+		\resizebox{!}{1.75em}{$\begin{aligned} 
+			\dot x &=-9.945x + 9.975y \\ 
+			\dot y &= 27.063x  -0.674y  -0.977xz\\ 
+			\dot z &= -2.649z + 0.996xy
+		\end{aligned}$}
 	\end{minipage}%
-	\begin{minipage}{0.47\textwidth}
+	\begin{minipage}{0.32\textwidth}
+		\[ \eta = 0.1, \, \lambda = 0.4, \]
+		\[ \varepsilon = 0.00301 \]
 		\begin{center}
-			\includegraphics[width = \textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{lorenz_found_001_tvdiff.png}
-
-			With total-variation regularization derivative
+			\includegraphics[width = 0.95\textwidth, trim={4.3cm, 1.6cm, 4.3cm, 2.5cm}, clip]{found_lorenz_01.pdf}
 		\end{center}
+		\resizebox{!}{1.75em}{$\begin{aligned} 
+			\dot x &= -9.800x + 9.832y \\ 
+			\dot y &= 25.948x  -0.438y -0.947xz \\ 
+			\dot z &= -2.615z + 0.983xy
+		\end{aligned} $}
+	\end{minipage}%
+	\begin{minipage}{0.32\textwidth}
+		\[ \eta = 1, \, \lambda = 0.416, \]
+		\[ \varepsilon = 0.21021 \]
+		\begin{center}
+			\includegraphics[width = 0.95\textwidth, trim={4.3cm, 1.6cm, 4.3cm, 2.5cm}, clip]{found_lorenz_1.pdf}
+		\end{center}
+		\resizebox{!}{1.75em}{$\begin{aligned} 
+			\dot x &= -7.007x + 7.148y  \\ 
+			\dot y &= 14.836x + 1.578y  -0.631xz \\ 
+			\dot z &=   -2.149z + 0.839xy -2.150
+		\end{aligned}$}
 	\end{minipage}
@@
 
-\begin{figure}[h]
-	\caption{Discovered Lorenz system with noise $\eta = 0.1$ and total-variation regularization differentiation}
-	\label{fig:lorenz_system_found_01}
+We can see that for the three noise levels, SINDy was able to correctly identify the qualitative behavior of the Lorenz system. 
+Further, SINDy identifies exclusively the correct terms in the systems for $\eta = 0.01$ and $\eta = 0.1$, deviating from the expected terms in $\eta = 1$ by a forcing term in the $\dot z$ equation (Figure \ref{fig:found_lorenz_systems}).
+Additionally, we notice that error in the produced system increases with noise, as we may expect, but additionally that this increase in error is not linear with noise.
+In particular, while the $\eta = 0.1$ system has approximately 10-fold the error as the $\eta = 0.01$ system, the $\eta = 1$ system sees an 100-fold increase in error over $\eta = 0.1$.
 
-	\centering
-	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{lorenz_found_01_tvdiff.png}
-\end{figure}
+For completeness, we note that for the $\eta = 0.01$ system, we use the basis $$\mathcal B = \{ \mathbf 1, \mathbf X, \mathbf X^{P_2}, \ldots, \mathbf X^{P_7}, \sin(1\mathbf X), \ldots, \sin{10\mathbf X}, \cos{1\mathbf X}, \ldots, \cos{10\mathbf X} \}.$$ We use a smaller basis for $\eta = 0.1$, $$\mathcal B = \{  \mathbf 1, \mathbf X, \mathbf X^{P_2}, \ldots, \mathbf X^{P_5}, \sin(1\mathbf X), \ldots, \sin{10\mathbf X}, \cos{1\mathbf X}, \ldots, \cos{10\mathbf X}\},$$
+and a smaller basis still for $\eta = 1$, 
+\[ \mathcal B = \{ \mathbf 1, \mathbf X, \mathbf X^{P_2}, \ldots, \mathbf X^{P_5} \}. \]
+The choice of basis was motivated by accuracy concerns with the higher levels of noise. For a larger discussion of the basis choice, see Appendix \ref{apx:lorenz_with_diff_bases}.
 
-We see that the SINDy algorithm was able to effectively capture the attracting dynamics present in the Lorenz system in all cases.
-Furthermore, for the standard derivative and noise $\eta = 0.01$, the discovered system had the form
-\begin{equation} \label{eq:found_lorenz_001}
-	\begin{split}
-		\dot x &= -9.982573809940325x + 9.999536628579511y, \\
-	\dot y &= 27.573169299598813x - 0.8370109395705518y - 0.98935201514641xz, \\
-	\dot z &= -2.660754272317803z + 0.9988807483584906xy.
-	\end{split}
-\end{equation}
-Comparing this result to the actual system (Equation \ref{eq:lorenz}), we see that the discovered system has perfectly identified the polynomial terms in the system with coefficients that are almost identical.
-We see similar strength in identifying the system for $\eta = 0.01$ (Equation \ref{eq:found_lorenz_001_tv}) and $\eta = 0.1$ (Equation \ref{eq:found_lorenz_01_tv}) systems with total-variation regularization derivatives.
-\begin{equation} \label{eq:found_lorenz_001_tv}
-	\begin{split}
-		\dot x &= -9.946417397865872x + 9.97621578174998y, \\
-		\dot y &= 27.0485300793758x - 0.670689440675418y - 0.976667757332429xz, \\
-		\dot z &= -2.6495215942228163z + 0.996381152512881xy.
-	\end{split}
-\end{equation}
-\begin{equation} \label{eq:found_lorenz_01_tv}
-	\begin{split}
-		\dot x &= -9.805048724434341x + 9.835722669096466y, \\
-		\dot y &= 25.92133086771059x - 0.433587521465246y - 0.946115512156319xz, \\
-		\dot z &= -1.930341755171950 - 2.54324607967731z + 0.983562354075398xy.
-	\end{split}
-\end{equation}
-
-We do see a forcing term introduced in the higher noise, $\eta = 0.1$, system for $\dot z$ which represents a term not present in actual system or the other two discovered systems.
-Though decreased performance is expected with higher noise.
-
-\subsection{Bifurcations: The Hopf normal form}
-In addition to SINDy's ability to extract the system dynamics from the chaotic Lorenz attractor (\ref{sec:lorenz_results}), Section \ref{sec:SINDy} discussed how Brunton et al.
-discussed a modification to SINDy which would allow the detection of bifurcations in a system \cite{sindy}.
-Similar to the authors, I will demonstrate this using the Hopf normal form:
+\subsection{Bifurcations: The Hopf normal form} \label{sec:hopf_results}
+In addition to SINDy's ability to recover the qualitatively similar dynamics to the chaotic Lorenz attractor, simple modifications to the SINDy algorithm, as discussed in Section \ref{sec:SINDy}, can allow SINDy to find bifurcations present in a system.
+As a case study on this ability, I will investigate the Hopf normal form and SINDy's ability to reconstruct the Hopf bifurcation present in the system.
+The Hopf normal form is given by the governing equations in (\ref{eq:hopf_normal}).
 \begin{equation} \label{eq:hopf_normal}
@@
 \end{equation} 
-While $\mu$ is the bifurcation parameter and will be varried, I will take $\omega = A = 1$.
-In order for SINDy to discover the bifurcation in its system, we have to collect data over a range of $\mu$ values.
-In particular, I collected data for 16 values of $\mu$ between $-0.2$ and $0.55$, with a Hopf bifurcation occurring when $\mu = 0$.
-For negative values of $\mu$, I collected data with the initial condition $(x_0,y_0) = (2,0)$, while for positive values data was collected both for this initial condition and for $(x_0, y_0) = (0.01, 0)$ in order to capture the limit cycle behavior.
-Further, all collected data was given noise of magnitude $\eta = 0.005$.
+In this section, I take parameter values $\omega = A = 1$, and collect data over a range of values for $\mu$, the bifurcation parameter (note the bifurcation occurs when $\mu$ goes from negative to positive).
+A bifurcation diagram of the Hopf normal form can be seen in Figure \ref{fig:hopf_normal_form}. 
+\begin{figure}[h]
+	\caption{Bifurcation diagram for the Hopf normal form. Blue orbits have initial condition $(x_0, y_0) = (2,0)$ and red orbits have initial condition $(x_0, y_0) = (0.01, 0)$. 
+	$\mu$ takes on values $\mu \in \{-0.2, -0.15, -0.1, -0.05, 0, 0.05, 0.1, 0.15, 0.2 \}$.}
+	\label{fig:hopf_normal_form}
+	\centering
 
-In order to account for multiple orbits worth of data, the derivatives for each orbit were calculated separately using the total-variation regularization derivative.
-Then, the $\mathbf X$ and $\mathbf {\dot X}$ matrices for all orbits were combined into a single data and derivative matrix.
-These could then be passed through SINDy as previously.
-For this example, a basis of all polynomials through 5th degree was used, with sparsity parameter $\lambda = 0.25$ and $10$ iterations of the sparse regression.
-Figure \ref{fig:discovered_hopf_0005} shows the discovered system as various values of $\mu$ and its ability to detect the Hopf bifurcation.
+	\includegraphics[width = 0.7\textwidth, trim={4.3cm, 2cm, 4.2cm, 3cm}, clip]{hopf_normal_actual.pdf}
+
+\end{figure}
+For sampling data from the system, I sampled from 17 values of $\mu$ between $\mu = -0.3$ and $\mu = 0.55$, where for negative values of $\mu$ I took one initial condition in a neighborhood of $(x_0, y_0) = (2, 0)$, while for positive values of $\mu$ I took one orbit form an initial condition in that neighborhood, and one from a neighborhood around $(x_0, y_0) = (0.01,0)$.
+In particular, the initial conditions were picked by some random perturbation from $(2,0)$ and $(0.01, 0)$ in order to achieve more diversity in the data.
+Finally, noise with magnitude $\eta = 0.005$ was applied to all collected data and $10\%$ of the data was withheld for error reporting.  
+All derivatives were computed using the total-variation regularization derivative to reduce the effect of noise.
+A basis of all $5$th-degree polynomials was used with sparsity parameter $\lambda = 0.6$.
+The resulting system is shown in Figure \ref{fig:discovered_hopf_0005}.
 
 \begin{figure}[h]
-	\caption{Discovered Hopf bifurcation. Blue orbits start at $(x_0, y_0) = (2,0)$ and red orbits start at $(x_0, y_0) = (0.01, 0)$.}
+	\caption{Discovered Hopf bifurcation with noise $\eta = 0.005$.
+Blue orbits have initial condition $(x_0, y_0) = (2,0)$ and red orbits have initial condition $(x_0, y_0) = (0.01, 0)$.
+Error, calculated as described in Section \ref{sec:measuring_error}, is $\varepsilon = 0.00913$.}
 	\label{fig:discovered_hopf_0005}
@@
 
-	\includegraphics[width = 0.7\textwidth, trim={4.3cm, 1.9cm, 4.3cm, 3.5cm}, clip]{found_hopf_bifurcation_0005.pdf}
+	\includegraphics[width = 0.7\textwidth, trim={4.3cm, 2cm, 4.2cm, 3cm}, clip]{found_hopf_bifurcation_0005.pdf}
+
+	\[ \begin{aligned}
+		\dot x &= -0.972y + 0.952x\mu -0.919x^3 -1.025xy^2 \\
+		\dot y &= 0.952x + 0.959y\mu -0.946y x^2 -0.956y^3 + 0.629\mu x y^2 -0.624xy^2\mu^2
+	\end{aligned} \]
+
 \end{figure}
 
-Furthermore, SINDy found the system to be given by
+Of particular interest, SINDy was able to correctly identify the qualitative behavior of the Hopf normal form, and the bifurcation occuring at $\mu = 0$.
+Additionally, it identified the correct basis terms for the $\dot x$ equation exactly, while for the $\dot y$ term it included an extra $\mu xy^2$ and $xy^2\mu^2$ terms.
+Additionally, the error measured in this system is higher than the noise observed in the Lorenz system for $\eta = 0.01$ and $\eta = 0.1$, both representing a larger magnitude of noise.
+This is indicative of different performance characteristics for SINDy depending on the system in question.
+We see this effect further with the Hopf normal form, as while the discovered Lorenz systems were similar with run-to-run noise variability, the Hopf normal form could have variable results with a different noise sample.
+In particular, we can see this in Figure \ref{fig:discovered_hopf_0005_2} where a different noise sample increases the error by about 3-fold, and changes the erronous terms identified by SINDy.
 
-\begin{equation}\label{eq:discovered_hopf_0005}
-	\begin{split}
-		\dot x &= -0.9916y + 0.9314\mu x - 0.9178x^3 - 0.9178xy^2 - 0.3081x^4y, \\
-		\dot y &= 0.9972x + 0.9926\mu y - 0.9811x^2y - 0.9814y^3.
-	\end{split}
-\end{equation}
-Here we notice that barring the $-0.3081x^4y$ term in the equation for $\dot x$, the algorithm was able to identify the constants remarkably well and the nonlinear terms accurately. 
-Though, its important to note that depending on the noise added to the system, the resulting system can be significantly worse.
-In particular, Equation \ref{eq:bad_discovered_hopf_0005} resulted from the same parameters but with different noise applied.
-\begin{equation}\label{eq:bad_discovered_hopf_0005}
-	\begin{split}
-		\dot x &= -0.9971y + 0.8704\mu x - 0.8617x^3 - 0.9177xy^2 + 0.9186\mu x^2 y  - 0.2853 xy^3 \\
-		&\qquad - 0.9918 \mu x y^2 - 0.8546 x^4y + 1.2614 x^3y^2 - 1.0363 x^2y^3 + 1.0065 xy^4 \\ &\qquad + 0.5446\mu y^3 x, \\
-		\dot y &= 0.9968x + 0.9930\mu y - 0.9807x^2y - 0.9822 y^3.
-	\end{split}
-\end{equation}
-Interestingly, while $\dot y$ remained stable, $\dot x$ tends to me less stable.
-It is important to note, that while there are many additional higher-order polynomial terms, the qualatative behavior of the system is identical, still finding a Hopf bifurcation.
+\begin{figure}[H]
+	\caption{Discovered Hopf bifurcation with noise $\eta = 0.005$ (but different noise sample from Figure \ref{fig:discovered_hopf_0005}).
+Blue orbits have initial condition $(x_0, y_0) = (2,0)$ and red orbits have initial condition $(x_0, y_0) = (0.01, 0)$.
+Error, calculated as described in Section \ref{sec:measuring_error}, is $\varepsilon = 0.02902$.}
+	\label{fig:discovered_hopf_0005_2}
+
+	\centering
+
+	\includegraphics[width = 0.7\textwidth, trim={4.3cm, 2cm, 4.2cm, 3cm}, clip]{found_hopf_bifurcation_0005_2.pdf}
+
+	\[ \begin{aligned}
+		\dot x &= -0.971y + 0.940\mu x -0.911x^3 -1.148xy^2 + 0.674xy^2\mu^2 \\
+		\dot y &= 0.966x + 0.955\mu y -0.924x^2 y -0.955y^3
+	\end{aligned} \]
+
+\end{figure}
+
+\subsection{Determining the Sparsity Parameter} \label{sec:determining_lambda}
+Brunton et al. discuss the concept of picking the sparsity parameter, $\lambda$, on the ``Pareto front'' where we see a balancing of complexity and accuracy \cite{sindy}. 
+Such an approach involves picking $\lambda$ when we see a sharp increase in accuracy when increasing the complexity of the model. 
+We can see this jump in accuracy behavior in Figure \ref{fig:large_scale_sparsity_error}, where we see accuracy dramatically rise (an increase in the negative error) at a particular sparsity.
+
+\begin{figure}[H]
+	\caption{Measured sparsity (percent non-zero coefficients) graphed against the negative error ($\varepsilon$) as discussed in Section \ref{sec:measuring_error}.
+Parameterized by $\lambda$ between $14.98$ and $0$.}
+	\label{fig:large_scale_sparsity_error}
+	\centering
+
+	\includegraphics[width = 0.7\textwidth]{large_scale_error_sparsity.pdf}
+\end{figure}
+We additionally see another (proportionally similar in size) jump following the initial jump in accuracy (Figure \ref{fig:small_scale_sparsity_error}).
+\begin{figure}[h]
+	\caption{Measured sparsity (percent non-zero coefficients) graphed against the negative error ($\varepsilon$) as discussed in Section \ref{sec:measuring_error}.
+Parameterized by $\lambda$ between $0.943$ and $0$.}
+	\label{fig:small_scale_sparsity_error}
+	\centering
+
+	\includegraphics[width=0.7\textwidth]{small_scale_error_sparsity.pdf}
+
+\end{figure}
+The jumps in error occur at $\lambda = 0.9434$, $\lambda = 0.674$, $\lambda = 0.0599$, and $\lambda = 0.0300$.
+We can examine the performance of SINDy with each of these sparsity parameters (Figure \ref{fig:lambda_variation}) and see that in each case, a decrease in $\lambda$ corresponds to an additional term added in the found system.
+Indeed, the initial jump from $\lambda = 0.9434$ to $\lambda = 0.6739$ sees a jump to the identification of only the correct terms, while smaller values of $\lambda$ introduce extra terms evident of over-fitting.
+
+\begin{figure}[ptb]
+	\caption{Discovered Lorenz Systems with noise $\eta = 0.01$ across different sparsity parameters ($\lambda$) specific to jumps in error ($\varepsilon$).}
+	\label{fig:lambda_variation}
+	\centering
+
+	\begin{minipage}{0.47\textwidth}
+		\[ \lambda = 0.9434, \, \varepsilon = 0.00125 \] 
+		\begin{center}
+			\includegraphics[width=0.95\textwidth, trim={4.3cm, 1.6cm, 4.3cm, 2.5cm}, clip]{lorenz_lambda_1.pdf}
+		\end{center}
+		\[ \begin{aligned}
+			\dot x &= -9.945x + 9.975y \\
+			\dot y &= 25.393x -0.944xz\\ 
+			\dot z &= -2.649z + 0.996xy \\ 
+		\end{aligned} \]
+
+		\vspace{1em}
+
+		\[ \lambda = 0.0599, \, \varepsilon = 0.00038 \]
+		\begin{center}
+			\includegraphics[width=0.95\textwidth, trim={4.3cm, 1.6cm, 4.3cm, 2.5cm}, clip]{lorenz_lambda_3.pdf}
+		\end{center}
+		\[ \begin{aligned}
+			\dot x &= -9.945x + 9.975y \\ 
+			\dot y &= 27.0627x -0.674y  -0.977xz \\ 
+			\dot z &=  -2.578z + 0.996xy -1.910
+		\end{aligned} \]
+	\end{minipage}%
+	\begin{minipage}{0.47\textwidth}
+		\[ \lambda = 0.6739, \, \varepsilon = 0.00041 \]
+		\begin{center}
+			\includegraphics[width=0.95\textwidth, trim={4.3cm, 1.6cm, 4.3cm, 2.5cm}, clip]{lorenz_lambda_2.pdf}
+		\end{center}
+		\[ \begin{aligned}
+			\dot x &= -9.945x + 9.975y \\ 
+			\dot y &= 27.063x -0.674y  -0.977xz\\ 
+			\dot z &= -2.649z + 0.996xy\\ 
+		\end{aligned} \]
+
+		\vspace{1em}
+
+		\[ \lambda = 0.0300, \, \varepsilon = 0.00035 \]
+		\begin{center}
+			\includegraphics[width=0.95\textwidth, trim={4.3cm, 1.6cm, 4.3cm, 2.5cm}, clip]{lorenz_lambda_4.pdf}
+		\end{center}
+		\[ \begin{aligned}
+			\dot x &=-9.945x + 9.975y \\ 
+			\dot y &= 27.0627x -0.674y -0.977xz \\ 
+			\dot z &= 0.579 -2.720z + 0.038x^2 + 0.972xy
+		\end{aligned} \] 
+	\end{minipage}
+\end{figure}
+
+It is important to recognize that decreasing $\lambda$, in this case, is always leading to a decrease in error, $\varepsilon$.
+However, as we see the slow introduction of forcing terms, such a decrease in $\lambda$ can result in symptoms of over-fitting.
+Therefore, any automated finding of a sparsity parameter needs to consider the potential for such over-fitting, and adjust accordingly.
+
+From this, we may propose a simple algorithm for finding an ideal $\lambda$ for a given system.
+In particular, we start from $\lambda = 0$ and increase $\lambda$ by repeatedly choosing $\lambda$ to be the smallest element (plus some small constant) of our fit $\mathbf \Xi$.
+This allows us to quickly cycle through values of $\lambda$ that are guaranteed to change the fit.
+We look for a change in $\lambda$ that corresponds to a relatively large jump in error, $\varepsilon$.
+When we observe this jump, we can more precisely search the space between the two values of $\lambda$ where the jump occured to get the largest value of $\lambda$ that lies before the jump in error. 
+By doing this, we can search for an ideal value for $\lambda$ that attempts to avoid over-fitting. Effectively searching the space for the ``Pareto front'' desrcibed by Brunton et al. \cite{sindy}.
+
+By running this algorithm on the Lorenz systems described in Section \ref{sec:lorenz_results}, we find that it produces the same systems as shown in Figure \ref{fig:found_lorenz_systems}, though with $\lambda = 0.620024$, $\lambda = 0.920751$, and $\lambda = 0.414742$, respectively.
+These values for $\lambda$ are significantly larger (or very similar) to those used in \ref{sec:lorenz_results}, demonstrating that there is significant headroom in choosing values for $\lambda$.
+Additionally, with these values of $\lambda$ determined entirely algorithmically, whereas $\lambda$ values were chosen by hand in Section \ref{sec:lorenz_results}, we demonstrate suitability of this sparsity parameter finding algorithm.
 
 \section{Discussion} \label{sec:discussion}
+
+In writing a ground-up implementation of the SINDy algorithm, I was able to replicate much of the success found by Brunton et al. in their paper presenting SINDy \cite{sindy}. 
+In particular, I was able to demonstrate remarkable success in replicating the qualitative behavior of both chaotic systems (Figure \ref{fig:found_lorenz_systems}) as well as systems with bifurcations (Figure \ref{fig:discovered_hopf_0005} and Figure \ref{fig:discovered_hopf_0005_2}).
+Further, these examples demonstrated an ability for SINDy to correctly determine the function basis elements present in the governing equations for these systems. 
+In all, this demonstrates a remarkable ability for SINDy to be used to gleam insights into the underlying dynamics of a system when only time series data on the system is available.
+
+However, it is important to note that I observed run to run variability in the success of the SINDy algorithm as discussed in Section \ref{sec:hopf_results}.
+This demonstrates that SINDy can be particularly sensitive to noise depending on the system in question.
+Of particular concern is the potential increase in error from simply differently sampled noise (the example presented in this paper showed a 3-fold increase in error).
+This is additionally interesting as such variability in results was not found for the Lorenz system (Section \ref{sec:lorenz_results}).
+
+Another condition on the performance of the SINDy algorithm is the choice of basis.
+Brunton et al.
+emphasize the necessity of a properly chosen basis in their work \cite{sindy}, and I was also able to demonstrate this sensitivity to the basis chosen.
+A deeper discussion on the instability noticed for different bases when running SINDy on the Lorenz System is noted in Appendix \ref{apx:lorenz_with_diff_bases}, however as summary, the choice of basis is not simply in exhaustion of potential function candidates, but can also cause SINDy to perform worse if the solution is too sparse in the chosen basis.
+Further, SINDy can show instability with single function additions to the basis, and fails to perform at all when the basis doesn't contain the necessary function candidates.
+
+For these reasons, exploring methods to determine good bases for SINDy is a fruitful area of further exploration.
+If such methods could increase the stability of SINDy, they could dramatically improve its usability.
+Without trust in the solutions produced, particularly with possible variations simply down to noise, it would be difficult to deploy SINDy to an application where the derived system would need to be trusted.
+A possible extention to address these issues could also be in the form of active learning with the SINDy algorithm.
+Fasel et al.
+propose a modification to SINDy with control in order to implement said active learning into SINDy \cite{9683120}.
+Further, more investigations into the performance of SINDy in situations where the governing equations are not known would be useful, in order to determine the usefulness of SINDy when parameters have to be determined without a reference to the actual, underlying system.
+
+Despite the difficulties in the consistency of SINDy, the applications for such a system could be expansive.
+In systems where non-conventional dynamical systems may apply, an algorithm like SINDy could be used to create a guess at the underlying dynamics in order to improve projections.
+A situation such as the stock market may be an interesting area of study using SINDy, or a similar algorithm, as the dynamics of the stock market are heavily obfuscated and potentially such an algorithm could gleam useful information on the dynamics from just the data.
+Robotic applications such as surface finishing could also potentially benefit from an algorithm such as SINDy. 
+In particular, the response to pressure from the end-effector on a part could have implications on the quality of the ultimate finishing job. 
+If imperfect, but generally accurate systems could be constructed to model such feedback, it could greatly improve the robot's understanding of the part and how to finish it.
+
+In an effort to explore further systems where SINDy could be applied, I worked to use SINDy to recover the dynamics from a three-body gravitational system (three-body problem).
+This is another cannonical example of a chaotic system (like the Lorenz system).
+However, I was unable to find success with SINDy in this system, with the lowest error achieved being $\varepsilon = 14.755$.
+Part of the problem with applying SINDy to this particular system is the scale and frequency of extreme behavior present in the three-body system.
+This erratic behavior likely creates a difficult environment for SINDy to operate.
+Additionally, SINDy could be struggling due to this being the only system tested that does not use a strictly polynomial basis.
+In particular, this system has the cube of a vector norm in the demoninator of the governing equations, necessitating a much more complicated function basis then either the Lorenz system or the Hopf normal form.
+While I was unable to achieve success in this system, further exploration on the prospects of modeling the three-body problem with SINDy are likely required.
+Additionally, further investigation of modeling other systems could bring to light additional drawbacks with the SINDy algorithm.
+
+While the SINDy algorithm shows immense promise in its ability to identify these systems, questions of stability and ability to choose a proper basis remain.
+These concerns make SINDy more difficult to apply in real-world scenarios, where the actual underlying system is unknown.
+In these situations, it becomes less clear if the system SINDy finds is reasonable, and therefore whether or not a different basis (or parameter values) should be used.
+Though these concerns remain, SINDy is significantly more powerful than the algorithms that inspired it \cite{bongard}\cite{schmidt}.
+This trajectory suggests a promising future for dynamics recovery algorithms.
 
@@
 
+\appendix 
+\newpage 
+\section{Lorenz System with Different Bases} \label{apx:lorenz_with_diff_bases}
+It is important to illustrate the sensitivity of the SINDy algorithm on the chosen basis. For the Lorenz System, performance was strong for bases that included a sufficient array of polynomials. 
+In Figures \ref{fig:found_lorenz_ex_1}, \ref{fig:found_lorenz_ex_2}, \ref{fig:found_lorenz_ex_3}, and \ref{fig:found_lorenz_ex_4} we see the performance of SINDy with a bases comprised of only polynomials.
+All examples are using the same $\mathbf X$ and $\mathbf {\dot X}$ matrices, with noise $\eta = 0.1$, and using the total-variation regularization derivative.
+
+\begin{figure}[H]
+	\caption{Discovered Lorenz System with basis consisting of all polynomial nonlinearities up to 7th degree.
+Found system shown in Equation \ref{eq:discovered_lorenz_ex_1}.
+Error: $\varepsilon = 0.00297$.}
+	\label{fig:found_lorenz_ex_1}
+
+	\centering 
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.6cm, 4.3cm, 2.5cm}, clip]{lorenz_1_sol.pdf}
+
+	\begin{equation}\label{eq:discovered_lorenz_ex_1}
+		\begin{split}
+			\dot x &= -9.800x + 9.832y \\ 
+			\dot y &= 25.948x -0.438y  -0.947xz \\
+			\dot z &= -1.899  -2.544z + 0.983xy
+		\end{split}
+	\end{equation}
+\end{figure}
+\begin{figure}[H]
+	\caption{Discovered Lorenz System with basis consisting of all polynomial nonlinearities up to 5th degree.
+Found system shown in Equation \ref{eq:discovered_lorenz_ex_2}.
+Error: $\varepsilon = 0.00297$.}
+	\label{fig:found_lorenz_ex_2}
+
+	\centering 
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.6cm, 4.3cm, 2.5cm}, clip]{lorenz_2_sol.pdf}
+
+	\begin{equation}\label{eq:discovered_lorenz_ex_2}
+		\begin{split}
+			\dot x &= -9.800x + 9.832y \\ 
+			\dot y &= 25.948x -0.438y  -0.947xz \\
+			\dot z &= -1.899  -2.544z + 0.983xy
+		\end{split}
+	\end{equation}
+\end{figure}
+\begin{figure}[H]
+	\caption{Discovered Lorenz System with basis consisting of all polynomial nonlinearities up to 3th degree.
+Found system shown in Equation \ref{eq:discovered_lorenz_ex_3}.
+Error: $\varepsilon = 0.02392$.}
+	\label{fig:found_lorenz_ex_3}
+
+	\centering 
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.6cm, 4.3cm, 2.5cm}, clip]{lorenz_3_sol.pdf}
+
+	\begin{equation}\label{eq:discovered_lorenz_ex_3}
+		\begin{split}
+			\dot x &= -9.800x + 9.832y \\ 
+			\dot y &= 25.948x -0.438y  -0.947xz \\
+			\dot z &= -49.621 -0.485x^2 + 1.277xy
+		\end{split}
+	\end{equation}
+\end{figure}
+\begin{figure}[H]
+	\caption{Discovered Lorenz System with basis consisting of all polynomial nonlinearities up to 2th degree.
+Found system shown in Equation \ref{eq:discovered_lorenz_ex_4}.
+Error: $\varepsilon = 0.00320$.}
+	\label{fig:found_lorenz_ex_4}
+
+	\centering 
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.6cm, 4.3cm, 2.5cm}, clip]{lorenz_4_sol.pdf}
+
+	\begin{equation}\label{eq:discovered_lorenz_ex_4}
+		\begin{split}
+			\dot x &= -9.800x + 9.832y \\ 
+			\dot y &= 24.863x -0.925xz \\
+			\dot z &= -1.899  -2.544z + 0.983xy
+		\end{split}
+	\end{equation}
+\end{figure}
+
+We find that with all four choices of basis, the $\dot x$ equation remained identical.
+Further, the $\dot y$ equation remained identical across the first three choices of basis.
+This is all while the $\dot z$ equation showed the same result in the first and second bases, though for the last two it differed.
+This demonstrates a tendancy for SINDy to be more unstable in one of the state variables.
+Further, we note that while the basis in Figure \ref{fig:found_lorenz_ex_4} has the fewest polynomials, its error is of the same magnitude as the larger bases composed of 5th and 7th degree polynomials (Figures \ref{fig:found_lorenz_ex_2} and \ref{fig:found_lorenz_ex_1}), when the basis of third-degree polynomials performs an order of magnitude worse than the other three (Figure \ref{fig:found_lorenz_ex_3}).
+This is demonstrative of a particular sensitivity to the selected basis as this demonstrates that both increasing or decreasing the size of the basis can improve the performance of SINDy. 
+Furthermore, in two separate tests including exponentials in the function basis (i.e.
+$e^x$, $e^y$, and $e^z$), SINDy identified the zero map exclusively.
+This could be due to the sparsity parameter, $\lambda$, being too large for the application, but as a comparison to the other bases tested, $\lambda$ was held constant.
+This demonstrates further inconsistencies when selecting various bases.
+
+For completeness, when running SINDy with a basis that doesn't include any of the relevant terms, it is unable to identify a reasonable system.
+In particular, running SINDy with bases of only sines and cosines on the Lorenz System results in synthesized behavior completely distinct from the Lorenz System,
+as seen in Figure \ref{fig:found_lorenz_ex_7} and Figure \ref{fig:found_lorenz_ex_8}.
+\begin{figure}[H]
+	\caption{Discovered Lorenz System with basis $\mathcal B = \{ \sin{ku_i}, \cos{ku_i} \ | \ k \in 1, \ldots, 10, u_i \in \{x,y,z\} \}$. Error: $\varepsilon = 1.72647$.}
+	\label{fig:found_lorenz_ex_7}
+
+	\centering 
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.6cm, 4.3cm, 2.5cm}, clip]{lorenz_7_sol.pdf}
+
+\end{figure}
+\begin{figure}[H]
+	\caption{Discovered Lorenz System with basis $\mathcal B = \{ \sin{ku_i}, \cos{ku_i} \ | \ k \in 1, \ldots, 50, u_i \in \{x,y,z\} \}$. Error: $\varepsilon = 1.73124$.}
+	\label{fig:found_lorenz_ex_8}
+
+	\centering 
+	\includegraphics[width = 0.47\textwidth, trim={4.3cm, 1.6cm, 4.3cm, 2.5cm}, clip]{lorenz_8_sol.pdf}
+
+\end{figure}
+
+Additionally, these systems show high error consistent with poor fits.
+
 \newpage

### 2024-04-30 Code/DynamicsRecovery/src/DynamicsRecovery.jl

@@ -16,7 +16,6 @@ include("SINDy/SINDy.jl")
 using .SINDy
 export constructX, Θ, sparse_regression
 export TvDiffParams
-export active_SINDy, measure_accuracy, measure_sparsity, get_testing_X
-
+export active_SINDy, measure_accuracy, measure_sparsity, get_testing_X, pareto_sparsity_accuracy, automatic_lambda_fitting
 
 end # module DynamicsRecovery

### 2024-04-30 Code/DynamicsRecovery/src/SINDy/SINDy.jl

@@ -13,7 +13,7 @@ export sparse_regression
 
 include("sparse_regression.jl")
 
-export active_SINDy, measure_accuracy, measure_sparsity, get_testing_X
+export active_SINDy, measure_accuracy, measure_sparsity, get_testing_X, pareto_sparsity_accuracy, automatic_lambda_fitting
 
 include("active_algorithm.jl")
 

### 2024-04-30 Code/DynamicsRecovery/src/SINDy/active_algorithm.jl

@@ -5,8 +5,93 @@ using StatsBase
 
 using DynamicsRecovery.Systems
 
-# function λ_sparsity_fitting(λ0, X::Matrix{Float64}, Xdot::Matrix{Float64}, X_test::Matrix{Float64}, Xdot_test::Matrix{{Float64}})
-# end 
+function automatic_lambda_fitting(X::Matrix{Float64}, Xdot::Matrix{Float64}, X_test::Matrix{Float64}, Xdot_test::Matrix{Float64}, Θx; kmax = 10, expected_multiple = 2.5, epsilon = 1e-2, proportional_λ_steps = 10, stopping_lambda = 10., polynomials = [], functions = [], functions1 = [])
+    # initial lambda, Xi, and error
+    λ = 0. # start at 0
+    Ξ= sparse_regression(Θx, Xdot, λ, kmax)
+    ε = measure_accuracy(Ξ, X_test, Xdot_test; polynomials = polynomials, functions = functions, functions1 = functions1)
+    previous_ε = ε 
+
+    previous_λ = 0.
+    # loop until we see an expected jump
+    while (previous_ε * expected_multiple > ε || previous_λ == 0 || λ == 0)
+        @info "λ = " * string(λ) * ", ε = " * string(ε)
+        previous_λ = λ # save previous value 
+
+        λ = minimum(abs.(Ξ[Ξ .!= 0])) + epsilon # to guarantee remove a coefficient, take the minimum value in Xi plus some tiny epsilon
+        Ξ = sparse_regression(Θx, Xdot, λ, kmax)
+
+        previous_ε = ε
+        ε = measure_accuracy(Ξ, X_test, Xdot_test; polynomials = polynomials, functions = functions, functions1 = functions1)
+
+        # failsafe
+        if λ > stopping_lambda 
+            return (λ, Ξ)
+        end # if
+    end # while
+
+    @info "Found jump in error at λ = " * string(λ)
+
+    initial_guess_min = previous_λ # save in case
+    initial_guess_max = λ # save in case
+
+
+    # more fine adjustment of λ
+    λ_step = (λ - previous_λ)/proportional_λ_steps
+    λ = previous_λ
+    Ξ = sparse_regression(Θx, Xdot, λ, kmax)
+    previous_Ξ = Ξ
+    initial_guess_min_Ξ = Ξ # save in case
+    ε = measure_accuracy(Ξ, X_test, Xdot_test; polynomials = polynomials, functions = functions, functions1 = functions1)
[…]

### 2024-04-30 Code/DynamicsRecovery/src/SINDy/library_construction.jl

@@ -23,13 +23,19 @@ function Θ(X::Matrix{Float64};
 
     polynomial_functions = construct_polynomials(polynomials, size(X)[2])
 
-    append!(functions, polynomial_functions)
+    # append!(functions, polynomial_functions)
 
     for func in functions 
         push!(function_library,
             hcat([func(X[i, :]...) for i in 1:size(X)[1]]) # hcat is to convert to matrix 
         )
     end # for func
+
+    for func in polynomial_functions 
+        push!(function_library,
+            hcat([func(X[i, :]...) for i in 1:size(X)[1]]) # hcat is to convert to matrix 
+        )
+    end # for func 
 
     # for functions1, just apply the function to all items in X 
     for func1 in functions1

### 2024-04-30 Code/DynamicsRecovery/src/SINDy/sparse_regression.jl

@@ -4,9 +4,17 @@ function sparse_regression(Θ::Matrix{Float64}, Xdot::Matrix{Float64}, λ::Float
     # create initial guess for Xi as just regression
     Ξ = Θ\Xdot
 
+
+    previous_small_coefficients_count = 0
     for _ in 1:kmax 
         # find coefficients that are less than λ 
         small_coefficients = abs.(Ξ) .< λ
+
+        # check for no change in small coefficients
+        if sum(small_coefficients) == previous_small_coefficients_count 
+            break 
+        end # if
+        previous_small_coefficients_count = sum(small_coefficients)
 
         # set small coefficients to 0 
         Ξ[small_coefficients] .= 0

### 2024-04-30 Code/DynamicsRecovery/src/Systems/solve_constructed_system.jl

@@ -12,8 +12,11 @@ end # function solve_constructed_system
 
 function get_constructed_system(Ξ; polynomials = [], functions = [], functions1 = [])
 
+    funcs::Vector{Any} = deepcopy(functions)
+    println(typeof(funcs))
+
     # add polynomials terms
-    append!(functions, construct_polynomials(polynomials, size(Ξ)[2]))
+    append!(funcs, construct_polynomials(polynomials, size(Ξ)[2]))
 
     # add functions in functions1
     for func in functions1
@@ -21,9 +24,20 @@ function get_constructed_system(Ξ; polynomials = [], functions = [], functions1
             # call function on the nth variable
             f(x...) = func(x[n])
 
-            push!(functions, f)
+            push!(funcs, f)
         end # for n
     end # for func
+
+    # polys = construct_polynomials(polynomials, size(Ξ)[2])
+    # println(typeof(polys))
+    # for func in polys
+    #     for n in 1:size(Ξ)[2]
+    #         # call function on the nth variable
+    #         f(x...) = func(x[n])
+
+    #         push!(funcs, f)
+    #     end # for n
+    # end # for func
 
     # strip out only relevant functions
     relevant_functions::Vector{Vector{Any}} = []
@@ -33,13 +47,13 @@ function get_constructed_system(Ξ; polynomials = [], functions = [], functions1
         n_rel_funcs = []
         n_rel_funcs_coef = []
         
-        for i in 1:length(functions)
+        for i in 1:length(funcs)
             # skip if the coefficient is 0
             if Ξ[i, n] == 0
                 continue
             end # if 
 
-            push!(n_rel_funcs, functions[i])
+            push!(n_rel_funcs, funcs[i])
             push!(n_rel_funcs_coef, Ξ[i, n])
         end # for i
 

### 2024-04-30 Code/DynamicsRecovery/src/Utils/Utils.jl

@@ -7,5 +7,4 @@ include("construct_polynomial_functions.jl")
 export print_constructed_system
 
 include("print_constructed_system.jl")
-
 end # module Utils

### 2024-04-30 Code/main_pluto.jl

@@ -85,7 +85,19 @@ add_theme(:custom, custom_theme)
 end
 
 # ╔═╡ c2016647-3b10-4041-a584-920ab5c116d1
-theme(:custom)
+# theme(:custom)
+theme(:default)
+
+# ╔═╡ 0d836d4e-d9d2-4fa1-9983-e541fb58ab04
+function sin_cos_function_library(k)
+	funcs = []
+	for i in 1:k
+		sink(x) = sin(i*x)
+		cosk(x) = cos(i*x)
+		append!(funcs, [sink, cosk])
+	end
+	funcs
+end
 
 # ╔═╡ 61ccdc43-c12f-4b59-b746-316c82b342a5
 md"""
@@ -102,7 +114,7 @@ begin
 end
 
 # ╔═╡ 4cbdb8af-68ca-421f-853c-5bd8c4f4b464
-plot(lorenz_system, idxs=(1,2,3), legend = false, xlabel = "", ylabel = "", zlabel = "", camera=(40,30), axis = ([], false), color=colorant"#00acff") # , xlabel = "x", ylabel = "y", zlabel = "z"
+plot(lorenz_system, idxs=(1,2,3), legend = false, xlabel = L"x", ylabel = L"y", zlabel = L"z", camera=(40,30), color=colorant"#00acff") # , xlabel = "x", ylabel = "y", zlabel = "z", axis = ([], false)
 
 # ╔═╡ 7970ebf4-794c-41d0-979b-7e2f83163fad
 # Plots.savefig("./lorenz_attractor.pdf")
@@ -147,51 +159,6 @@ begin
 	X_lorenz_1_td, Xdot_lorenz_1_td, X_lorenz_1_td_test, Xdot_lorenz_1_td_test = get_testing_X(X_lorenz_1, Xdot_lorenz_1, 0.1)
 end
 
-# ╔═╡ b5b84157-9a8e-4cf7-97f0-5e8f168d15b9
-begin 
-	lorenz_1_td_polynomials = collect(0:5)
-	lorenz_1_td_functions1 = [] #[sin_cos_function_library(10)...]
-	
-	Θ_lorenz_1_td = Θ(X_lorenz_1_td; polynomials=lorenz_1_td_polynomials, functions1 = lorenz_1_td_functions1)
-
-	Ξ_lorenz_1_td = sparse_regression(Θ_lorenz_1_td, Xdot_lorenz_1_td, 0.25, 10)
[…]
